\subsection{Prof. Dr. Matthijs Bogaards}


\textbf{Main Research Interests}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Comparative Politics
\item[$\bullet$]	Democratization
\item[$\bullet$]	Political Parties
\item[$\bullet$]	Electoral Systems 
\item[$\bullet$]	Divided Societies
\end{enumerate}

\vspace{0.6cm}
\textbf{Research Activities}\\[-0.25cm]

In 2006, Matthijs Bogaards presented papers at various international conferences: at the tri-annual world conference of the International Political Science Association in Japan, at the annual meeting of the Swiss Political Science Association in Switzerland, and at a workshop in Institute Clingendael in the Netherlands organized by the hosts together with the United Nations University Tokyo and International IDEA of Stockholm. The topics of these papers reflect the wide ranging research interests of Matthijs Bogaards, which at the moment focus on the question of how to measure democracy and how to design democratic political institutions in divided societies. In 2006, Matthijs Bogaards finished three publications that will appear in international peer-reviewed political science journals in 2007. Following up on their successful workshop at the ECPR Joint Sessions in Granada in 2005 and two panels at the ECPR General Conference in Budapest later that year, Matthijs Bogaards and Françoise Boucek prepared an edited volume on \textit{Dominant Parties and Democracy}. A book proposal was submitted to Routledge. Finally, Matthijs Bogaards started writing a research monograph for Palgrave Macmillan with the title \textit{Democracy and Social Peace in Divided Societies: A Comparative Exploration of Power-Sharing Parties}. 


\vspace{0.6cm}
\textbf{Funded Projects}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	\textit{Managing Ethnic Conflict through Institutional Engineering: Ethnic Party Bans in Africa}\newline
(together with Dr. Matthias Basedau, Institut für Afrika-Kunde, 	Hamburg, Prof. Dr. Peter Niesen, Technical University Darmstadt, and 	Prof. Dr. Christoph Hartmann, University Bochum) \newline
funded by Thyssen Foundation
\end{enumerate}


\vspace{0.6cm}
\textbf{Other Professional Activities}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Guest-editor of a special issue on 'Democracy and Power-Sharing in Multinational States' of the UNESCO \textit{International Journal of Multicultural Societies}, 8(2), 2006.
\item[$\bullet$]	Reviewer for \textit{European Journal of Political Research, Government \& 	Opposition, Journal of Politics, Journal of Theoretical Politics, Nations 	and Nationalism}
\item[$\bullet$]	Member of the Faculty Council at IUB
\end{enumerate}


\vspace{0.6cm}
\textbf{PhD-Students}\\[-0.25cm]

Sebastian Elischer \newline
\textit{Political Parties, Party Systems and Electoral Cleavages in Africa}
