\subsection[Prof. Dr. Jan Delhey]{Prof. Dr. Jan Delhey{\normalfont\normalsize\newline (Joined IUB in September 2006)}}

\vspace{0.3cm}
\textbf{Main Research Interests}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Social Inequality and Stratification
\item[$\bullet$]	Quality of Life and Subjective Well-being
\item[$\bullet$]	Social Capital and Trust
\item[$\bullet$]	Political Sociology of European Integration
\end{enumerate}


\vspace{0.6cm}
\textbf{Research Activities}\\[-0.25cm]

A first cluster of research activities of Jan Delhey was concerned with trust between European nations. On the one hand, the impact enlargements have had on the social cohesion of the European Union (EU), measured as generalized interpersonal trust between EU nationalities, has been explored. The key result is that enlargements do not necessarily weaken cohesion, but southern enlargement and the recent eastern enlargement did. The integrative effect of enlargement depends on the extent to which acceding nations differ from existing club members in three main dimensions: the level of modernization (mechanisms: prestige), cultural characteristics (mechanisms: similarity) and their power in the international system (mechanisms: perceived threat). On the other hand, the role of cross-border transaction for shaping trust in other nations has been explored. The main finding is that transactions are not key for trust in other nations. A second cluster of Jan Delhey's activities was concerned with life satisfaction. The main interest here was the effect of cross-border comparisons on individual happiness, which is a journey into unknown territory - the EU as a possible yardstick for national living conditions. Main findings are that large segments of EU-citizens are able to rate their country vis-à-vis EU average, and country-EU-comparisons are salient to life satisfaction - perceptions of deprivation or gratifications can make people more unhappy or more happy.


\vspace{0.6cm}
\textbf{Organization of Scientific Conferences}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	October 2006\newline
	Kassel\newline
	Congress of the Deutsche Gesellschaft für Soziologie (DGS)\newline
	Organizer of an ad hoc group "Sociology of European Integration"
\end{enumerate}


\vspace{0.6cm}
\textbf{Other Professional Activities}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Board member of \textit{Journal of Happiness Studies}
\end{enumerate}