\subsection{Prof. Dr. Adalbert F.X. Wilhelm}


\textbf{Main Research Interests}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Exploratory Data Analysis and Statistical Modeling
\item[$\bullet$]	Interactive Statistical Graphics
\item[$\bullet$]	Information Visualization and Visual Data Mining
\item[$\bullet$]	Knowledge Management in Web-based Communities
\item[$\bullet$]	Computational Statistics
\end{enumerate}

\vspace{0.6cm}
\textbf{Research Activities}\\[-0.25cm]

As in previous years, Adalbert Wilhelm focused in his research on exploratory approaches to data analysis and modeling. The collaboration within the Key Visuals Project has been continued and some initial data exploration has been performed to detect structures in the semantic information of video material that has been annotated by mass communication scholars. Data Mining procedures like association rules and classification trees have been adapted to investigate relationships and rules within the semantic information. Some heuristics have been developed to devise representative samples of web pages and annual reviews in this context. The behavior of various cluster analysis techniques has been studied and a new complex cluster scheme has been devised which is currently in the implementation phase. Based on prior research in the area of knowledge management the focus has been shifted on incorporating the aspect of innovation into the framework of online-knowledge communities. The major research question is, how innovation processes can be optimally supported in the cooperative context of private-public Communities of Practice. Within this framework, the research focuses on the factors that influence, support, and stimulate innovation processes - as measured by the three constructs (knowledge transfer, knowledge communication and knowledge creation).


\vspace{0.6cm}
\textbf{Other Professional Activities}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Reviewer for SFI, Science Foundation Ireland
\item[$\bullet$]	Associate Editor \textit{Computational Statistics and Data Analysis}
\item[$\bullet$]	Associate Editor \textit{Computational Statistics}
\item[$\bullet$]	Associate Editor \textit{Journal of Computational and Graphical Statistics}
\item[$\bullet$]	Vertrauensdozent der \textit{Stiftung der Deutschen Wirtschaft}
\end{enumerate}


\vspace{0.6cm}
\textbf{Research Personnel}\\[-0.25cm]

Felix Schmitz-Justen, Ph.D.
