\section{A Lifespan Perspective on Organizational Behavior}
\shorttitle{A Lifespan Perspective on Organizational Behavior}

Organizational behavior research addresses the interplay of organizational context - expressed in an organization's culture, climates and goals - and organization members' KSAOs - the I/O Psychology shorthand for knowledge, skills, abilities and other characteristics (e.g., motives, personality, values). Until recently, age-related KSAO changes have not been much of a concern. The business place has been - and still is - youth-centered, and research projects have reflected this. In the wake of demographic change, however, a growing number of older (50+ yrs) workers will live longer work lives. At the same time, fewer younger workers will be available. As globalization and technological change pace permanent adaptation, continuous learning will become an integral part of organizations' operating systems. 

 On this background, an important overarching question will be how the developments of an organization and of its members may best be aligned for the benefit of both sides. More specifically, a fruitful research agendum will be to apply concepts and findings from lifespan psychology to develop an age-differentiated theory that describes how organizational and individual learning needs and abilities can best be matched. With a view on individuals, this will require to uncover the system of age-related changes in workplace behaviors. With a view on companies, it will be necessary to develop competency management approaches that take the dynamics of individual development into account.

\subsection{Successful Workplace Learning across the Lifespan}

\input{LifespanWork}

\subsection{Dynamic Modeling of Lifelong Learning Competency}

\input{LifespanDyn}

\subsection{Organizational Determinants of Vocational Adjustment Disorders}

\input{LifespanOrg}

\subsection{Other Professional Activities}

\textit{Editorial Board Membership}

\begin{itemize}
\item Journal of Behavioural Sciences.
\end{itemize}

\textit{Ad-hoc Reviews}

\begin{itemize}
\item Journal of Behavioural Sciences.
\item Swiss National Fund.
\item Zeitschrift f\"ur Personalpsychologie.
\item Zeitschrift f\"ur Sozialpsychologie.
\end{itemize}




