\section{The Mechanics and Pragmatics of Lifespan Development: Conceptualization, Measurement and Plasticity}
\shorttitle{Mechanics and Pragmatics of Lifespan Development}

According to modern notions of development such as the lifespan approach, human development is the result of the interaction between three different sources: biology (maturation/senescence), culture (learning), and an individual (decision/action). It is further assumed that psychological phenomena can be meaningfully and for heuristic purposes distinguished in those of the life mechanics and those of the life pragmatics (e.g., Staudinger \& Pasupathi, 2000). Life mechanics reflect individual differences in biology-based patterns of perception, information processing, emotion, and motivation (e.g., basic motivational (approach/avoidance) and emotional (positive/negative) patterns, temperament, speed of information processing, executive processes). Life pragmatics reflect individual differences in the accumulated and constructed experiences with the world (i.e., other people, events, circumstances, rules, places, and objects relevant for leading our lives) and with our self, as well as ways of dealing with the world and with ourselves (e.g., coping, emotion regulation, goal system). In the long run, it seems essential for our understanding of developmental processes to successfully decipher the co- and interaction of those two elements. Presently our research efforts however concentrate on the domain of life pragmatics. Life pragmatics can be distinguished in constructs related to insight and those related to compository or management strategies. With regard to insight, we study insight into life (life insight) as well as insight into our self (self-insight) and the highest form of both, that is, wisdom. With regard to compository strategies, we are especially interested in personal life investment, emotion regulation, coping and time experience. 

Life insights as well as life-compository structures and processes are not determined but plastic. Within a 'norm of reaction' better or worse developmental trajectories are conceivable. Given this basic contention of the plasticity of human development, it is crucial to determine the conditions of plasticity as well as its limits in different domains of psychological functioning. Thus, a third and fourth research focus concern themselves with the theoretical and empirical investigation of the plasticity of human development. The third focus concentrates on the effects of (in particular social) contexts on adult development and the fourth focus is primarily theoretical in nature. It explores the question of different types of plasticity, such as growth and resilience, and pursues the thesis that it is useful to distinguish two different kinds of positive adult development, one aiming towards growth and the other geared towards adjustment. In the following, these four research foci are described in turn.

\textbf{Central reference} Staudinger, U. M. \& Pasupathi, M. (2000). Lifespan perspectives on self, personality and social cognition. In T. A. Salthouse \& F. I. M. Craik (Eds.), The handbook of aging and cognition (pp. 633-688). Hillsdale, NJ: Erlbaum.

\subsection{Life Insight, Self Insight, and
Wisdom: Measurement, Age Trajectories}

\input{MechPragInsight}

\subsection{Life Composition: Measurement and Age Trajectories}

\input{MechLife}

\subsection{Context as a Facilitator of Adult Personality
Development}

\input{MechContext}

\newpage
\subsection{Plasticity and Positive Development: Theoretical and
Empirical Approaches}

\input{MechPlasticity}

\newpage
\subsection{Other Professional Activities}

\begin{itemize}
\item President elect German Psychological Association (DGPs).
\item Member of the Selection Committee of the Alexander von Humboldt Foundation.
\item Member and Vice-Chairperson of the Leopoldina and acatech Committee ``Aging-Work Education''. 
\item Senior Fellow of the International Network on Aging of the Max Planck Society (MAXNETAging).
\item Member of the Scientific Board of the German Center for Gerontology (DZA) in Berlin.
\item Member of Scientific Board Center Aging \& Work (Sloane Foundation).
\end{itemize}



\textit{Editorial Board Memberships}

Psychology and Aging (since 1997), Psychologie in Erziehung und Unterricht (since 2000), Psychologie Verlagsunion Book Series ``Psychologie-Forschung-Aktuell'' (2000-2005), Book Series Psychologische Diskurse (Verlag Vandenhoeck \& Ruprecht) (since 2003), Research in Human Development (since 2003), The Journal of Positive Psychology (since 2005), Developmental Science (since 2006).


