\hyphenation{Life-long}
\section{The Neuroscience and Human-Performance Perspective on
Lifelong Learning} \shorttitle{Neuroscience and Human Performance
}

  Our research focuses on identifying mechanisms underlying cortical plasticity and the structure-function relationships between cognitive, sensory, and motor performance and learning. The human brain remains plastic even at high age. However, plastic capacity declines with age. In this context the ability to facilitate plasticity is of high significance for the elder learner.
  
 In this context, research of our group is divided into three main topics:

 Our first interest is to investigate the plastic-adaptive capacity of the brain to understand basic mechanisms of plasticity and learning as well as the effects of age. Based on these experiments possible interventions might be developed to improve learning and to interfere with age-related decline. Fields of research are vibrotactile perceptual learning, force control and force modulation, motor-cognitive dual-task performance, intermanual transfer of learned motor programs, and the sensory-motor coupling during learning.
	
 Second, physical fitness is assumed to preserve cognitive functioning and psychological well-being in older adults. However, the mechanisms, the dose-response-relationship and also effects of different types of exercise are not well understood. Following an interdisciplinary view on human performance that comprises motor, neurophysiological, and psychological expertise and methods, the second area of research deals with the role of aerobic and acrobatic exercise on cognitive performance and well-being across the lifespan.
	
 Third, the plastic-adaptive capacities of the adult and aging brain are of particular importance for the aging work force. As part of joint JCLL efforts, combining our expertise in the above mentioned fields of research, we developed a research proposal to establish measures of older workers' adaptivity in the sensory, motor and cognitive domains and to relate their adaptive capabilities to the demands of the work place. From the results we will be able to identify mismatches between demands of the work place and individual preconditions. We assume that these mismatches might be used as predictors of low productivity or health problems of the employees.

\subsection{Plastic-Adaptive Capacity of the Brain: Mechanisms, Effects of Age, Possible Interventions}

\input{NeuroPlastic}

\subsection{Effects of Cardiovascular and Motor Fitness on Cognitive Performance and Well-Being in Older Adults}

\input{NeuroCardio}

\subsection{Awards, Fellowships}

\begin{itemize}
\item Junior Fellow of the Leopoldina-Acatech Working group ``Chancen und Probleme einer alternden Gesellschaft: Die Welt der Arbeit und des lebenslangen Lernens'' (Claudia Voelcker-Rehage).
\end{itemize}
 
\subsection{Other Professional Activities}

\textit{Ad-hoc Reviews}

\begin{itemize}
\item Godde, B.: \\Journal of Cognitive Neuroscience; Cognition; Quarterly Journal of Experimental Psychology, Journal of Neuroscience, Neuroscience and Biobehavioral Reviews; Experimental Brain Research; Journal of Neuroscience Methods; ACM Transactions on Applied Perception; Behavioural Brain Research.
\item Voelcker-Rehage, C.: \\European Review of Aging and Physical Activity.
\end{itemize}

