\section{The Socio-Economics of Lifelong Learning}
\shorttitle{Socio-economics of Lifelong Learning}

We define socio-economic research on lifelong learning as the combination of economic research, for example human capital formation and accumulation, with the sociological research of social processes. Market failure in the provision and investment in lifelong learning is our starting hypothesis. Our research group studies ``critical'' transitions over the life course and analyses the medium term impact of transitions on learning and employment careers. The life course perspective provides the central analytical tool, which allows us to study individual trajectories and the evolution of societies as a whole. 

 Our research focuses on (1) processes of social stratification as they are co-determined by learning processes for adults, (2) the sociology of education as the involvement of specific groups like migrants is concerned and (3) the ageing of the work force and implications for lifelong learning. Each of these fields is approached with an emphasis on the links between working and learning in modern societies as they concern individuals, households, firms and whole country systems. 

 We study transitions throughout the life course, which range from labor market entry, reentry after career breaks to gradual retirement with special attention on implications for aging societies. These social dynamics are modeled by use of a transition theory that is based on notions of coupled oscillations (Sch\"{o}mann and O'Connel 2002) and synchronization techniques, which are derived from dynamic systems theory. The rising importance of work-related lifelong learning in non-formal settings is studied through the comparisons of successful combinations of learning and working in firms and comparisons across the European Union. 

 Currently co-financed research projects deal with socioeconomic aspects of lifelong learning in two major areas: (1) lifelong learning and the labor market as well as (2) implications of ageing work forces for learning and working.

\subsection{Lifelong Learning and the Labor Market}

\input{SocioEcoLife}

\subsection{Implications of the Aging Workforce for Learning and Work} 

\input{SocioEcoImplic}

\subsection{Other Professional Activities}

\begin{itemize}
\item Consultant to OECD, European Commission DG Employment, Brussels and the European Foundation for the Improvement of Living and Working Conditions, Dublin.
\item Administrative Coordinator SISWO (Netherlands, 5th Framework Programme of the European Commission DG Research). 
\end{itemize}

\textit{Editorial Board Membership}

\begin{itemize}
\item Formation Emploi, Revue Fran\c caise de Sciences Sociales (since 2002).
\end{itemize}

 

