%the function for the book publication could be as follows [it was not implemented here]
%1=author;2=year;3=title;4=publisher + comments
%\newcommand{\book}[4]{#1 (#2). \textit{#3}. #4}

\subsection{Publications}




	\paragraph{Books} \textit{ }
\bigskip
	
Crewe, E., \& Müller, M.G. (2006). \textit{Rituals in parliaments. Political, anthropological and historical perspectives on Europe and the United States}. Frankfurt am Main: Peter Lang. \\ \\ 

Hurrelmann, A., Schneider, S., \& Steffek, J. (2006). \textit{Legitimacy in an age of global politics}. Basingstoke: Palgrave Macmillan, in press.\\ \\ 

Kesting, S. (2006). \textit{Transmission network access regulation in the European gas market} (Freiburger Studien zur Netzökonomie, Bd. 12), Baden-Baden: Nomos Verlag\\ \\ 

Ludes, P. (2006). \textit{Hegemonias Visuais - Una Introdução}. Salvador-Bahia: Hexis, in press.\\ \\ 

Pfaffenberger, W., \& Sioshansi, F.P. (Ed.) (2006). Electricity market reform: An international perspective. Amsterdam: Elsevier.\\ \\ 

Steffek, J. (2006). \textit{Embedded liberalism and its critics: Justifying global governance in the American century}. New York: Palgrave Macmillan.\\ \\ 

Steffek, J., Kissling, C., \& Nanz, P. (Eds.) (2006). \textit{Civil society participation in European and global governance: A cure for the democratic deficit?} Basingstoke: Palgrave Macmillan, in press.\\ \\ 




\paragraph{Articles \& Chapters}\textit{ }

\bigskip


Bausch, A. (2006). Branchen- und Wettbewerbsanalyse im strategischen Management. In D. Hahn, \& B. Taylor (Eds.), \textit{Strategische Unternehmungsführung - Strategische Unternehmungsplanung}, 9. Auflage (pp. 195-214). Berlin: Springer.\\ \\ 

Bausch, A., \& Krist, M. (2006). The effect of context-related moderators on the internationalization-performance relationship: Evidence from meta-analysis. \textit{Management International Review}, in press.\\ \\ 

Bausch, A., \& Rosenbusch, N. (2006). Innovation und Unternehmenserfolg: Eine meta-analytische Untersuchung. \textit{Die Unternehmung, 2}, 125-140.\\ \\ 

Boehnke, K., \& Welzel, C. (2006). Wertetransmission und Wertewandel: Eine explorative Drei-Generationen-Studie. \textit{Zeitschrift für Soziologie der Erziehung und Sozialisation, 26} (4), 341-360.\\ \\ 

Bogaards, M. (2006). Electoral systems, party systems, and ethnic conflict management in Africa. In M. Basedau, G. Erdmann, \& A. Mehler (Eds.),\textit{ Votes, money and violence: Political parties and elections in Africa}. (pp.169-194). Uppsala: Nordiska Afrikainstitutet.\\ \\ 

Brockmann, H. (2006). Können wir uns die demografische Alterung leisten? Altersrationierung und Generationengerechtigkeit am Beispiel des Krankenhauspatienten. In K.-S. Rehberg (Ed.), \textit{Soziale Ungleichheit, Kulturelle Unterschiede}. Verhandlungen des 32. Kongresses der Deutschen Gesellschaft für Soziologie in München 2004. Bd. 2. (pp. 1003-1021). Frankfurt am Main: Campus Verlag. \\ \\ 

Brockmann, H., Müller, R., \& Voges, W. (2006). Auch ein Reformeffekt? Eine exporative Analyse der zunehmenden Krankenhausbehandlungen auf Grund psychischer Störungen. \textit{Das Gesundheitswesen}, in press.\\ \\ 

Brüggemann, M., Sifft, S., Kleinen-v.Königslöw, K., Peters B., \& Wimmel, A. (2006). Segmentierte Europäisierung - Trends und Muster der Transnationalisierung von Öffentlichkeiten in Europa. In W.R. Langenbucher, \& M. Latzer (Ed.),\textit{ Europäische Öffentlichkeit und medialer Wandel. Eine transdisziplinäre Perspektive} (pp. 214-231). Wiesbaden: VS Verlag.\\ \\ 

Brunekreeft, G., \& Bauknecht, D. (2006). Energy policy and investment in the German power market. In F.P. Sioshansi, \& Pfaffenberger, W. (Eds.), \textit{Electricity market reform: An international perspective} (pp. 235-265). Amsterdam: Elsevier.\\ \\ 

Brunekreeft, G., \& Ehlers, E. (2006). Ownership unbundling of electricity distribution networks and distributed generation. \textit{Competition and Regulation in Network Industries, 1}, 63-86.\\ \\ 

Brunekreeft, G., \& Newbery, D.N. (2006). Should merchant transmission investment be subject to a must-offer provision? \textit{Journal of Regulatory Economics, 30}, in press.\\ \\ 

Brunekreeft, G., \& Müller, C. (2006). Der generelle X-Faktor in der Anreizregulierung. \textit{Energiewirtschaftliche Tagesfragen}, in press.\\ \\ 

Delhey, J., \& Kohler, U. (2006). From nationally bounded to pan-European inequalities? On the importance of foreign countries as reference groups. \textit{European Sociological Review, 22}, 125-140.\\ \\ 

Deutsch, F. (2006). Legitimacy and identity in the European Union. Empirical findings from the old member states. In I.P. Karolewski, \& V. Kaina (Eds.), \textit{European Identity. Theoretical Perspectives and Empirical Insights} (pp. 149-178). Berlin: LIT.\\ \\ 

Genschel, P., \& Uhl, S. (2006). Der Steuerstaat und die Globalisierung. In S. Leibfried, \& M. Zürn (Eds.), \textit{Transformation des Staates?} (pp. 92-119). Frankfurt am Main: Suhrkamp.\\ \\ 

Genschel, P., \& Ganghof, S. (2006). Taxation and democracy in the EU. \textit{Journal of European Public Policy}, in press.\\ \\ 

Friedrichs, J. (2006). Defining the international public enemy. The political struggle behind the legal debate on international terrorism. \textit{Leiden Journal of International Law, 19} (1), 69-91.\\ \\ 

Friedrichs, J. (2006). When push comes to shove. The territorial monopoly of force and the travails of neomedieval Europe. In M. Burgess, \& H. Vollaard (Eds.), \textit{State Territoriality and European Integration }(pp. 228-251). London: Routledge.\\ \\ 

Jachtenfuchs, M. (2006). Das Gewaltmonopol. Denationalisierung oder Fortbestand? In S. Leibfried, \& M. Zürn (Eds.), \textit{Transformation des Staates? }(pp. 69-91). Frankfurt am Main: Suhrkamp.\\ \\ 

Jachtenfuchs, M. (2006). The EU as a polity (II). In K. Jørgensen, E. Pollack, A. Mark, \& B. Rosamond (Eds.), \textit{Handbook of European Union Politics}. London: Sage, in press.\\ \\ 

Joppke, C. (2006). Citizenship between de- and re-ethnicization. In Y.M. Bodemann, \& G. Yurdakul (Eds.), \textit{Migration, Citizenship, Ethnos} (pp. 63-91). New York: Palgrave-Macmillan.\\ \\ 

Joppke, C. (2006). L'effacement du multiculturalisme dans l'Etat liberal. In R. Kastoryano (Ed.), \textit{Les codes de la Difference}. Paris: Presses de Sciences Po, in press.\\ \\ 

Joppke, C. (2006). Response to Saskia Sassen's "The Repositioning of Citizenship and Alienage". In K. Tunstall (Ed.), \textit{Displacement, asylum, migration} (pp. 204-209, 334-335). Oxford University Press.\\ \\ 

Joppke, C. (2006). Staatsbürgerschaft und kulturelle Differenz. In K.S. Rehberg (Ed.), \textit{Soziale Ungleichheit - Kulturelle Unterschiede}. Verhandlungen des 32. Kongresses der Deutschen Gesellschaft für Soziologie in München 2004 (pp. 797-812). Frankfurt am Main: Campus.\\ \\ 

Joppke, C. (2006). Exclusion in the liberal state (in Czech). \textit{Socialni Studia}, 11, in press.\\ \\ 

Kaina V., \& Deutsch, F. (2006). Verliert die "Stille Revolution" ihren Nachwuchs? Wertorientierungen in Deutschland im Kohorten- und Zeitvergleich. In E. Roller, F. Brettschneider, \& J.W. van Deth (Eds.),\textit{ Jugend und Politik: "Voll normal!". Der Beitrag der politischen Soziologie zur Jugendforschung} (pp. 157-181). Wiesbaden: VS Verlag für Sozialwissenschaften.\\ \\ 

Ludes, P. (2006). Existential truths as prerequisites for a globalizing discourse theory. In G. Backhaus, \& G. Psathas (Eds.), \textit{The sociology of radical commitment: Kurt H. Wolff's existential turn} (pp. 115-136). Lanham, MD: Lexington Books.\\ \\ 

Ludes, P. (2006). "Individual Transcendence, Media Transformations, and Collective Experiences: An Introduction to my 1984 Interview with Kurt H. Wolff" and "Surrender-and-Catch and Charismatic Authority: An Interview by Peter Ludes". In G. Backhaus, \& G. Psathas (Eds.), \textit{The sociology of radical commitment: Kurt H. Wolff's existential turn} (pp. 169-178). Lanham, MD: Lexington Books.\\ \\ 

Ludes P. (2006). A televisao: imagens-chave. In Universidade Federal da Bahia, VPC Cinema Video (Ed.), \textit{Seminário Internacional de Cinema e Audiovisual} (pp. 77-82). Salvador-Bahia : Universidade Federal.\\ \\ 

Müller, M.G., \& Özcan, E. (2006). The political iconography of Muhammad cartoons: Understanding conflict and political action. \textit{PS - Political Science and Politics}, in press.\\ \\ 

Müller, M.G., \& Kappas. A. (2006). Bild und Emotion: ein neues Forschungsfeld. Theoretische Ansätze aus Emotionspsychologie, Bildwissenschaft und visueller Kommunikationsforschung. \textit{Publizistik, 51}, 3-23.\\ \\ 

Müller, M.G. (2006). Die Ikonographie des politischen Händedrucks. In E. Wipfler (Ed.), \textit{Freundschaft. Motive und Bedeutungen} (pp. 205-217). Köln, Wien: Böhlau.\\ \\ 

Müller, M.G. (2006). Parliaments and their liturgies. In E. Crewe, \& M.G. Müller (Eds.), \textit{Rituals in parliaments. Political, anthropological and historical perspectives on Europe and the United States} (pp.183-206). Frankfurt am Main: Peter Lang.\\ \\ 

Müller, M.G. (2006). Politikberatung aus kommunikationswissenschaftlicher Perspektive. In S. Falk, D. Rehfeld, A. Römmele, \& M. Thunert (Eds.), \textit{Handbuch Politikberatung} (pp. 88-95). Wiesbaden: VS Verlag.\\ \\ 

Müller, M.G., \& Knieper, T. (2006). Texas bonfire traditions. The cartoon that got under fire. In M. Land, \& B.W. Hornaday (Eds.),\textit{ Contemporary Media Ethics} (pp. 277-292). Spokane: Marquette Books.\\ \\ 

Müller, M.G. (2006). Violent Visuals - Visual Violence. Gewaltbilder - Bildgewalt. \textit{In Ausstellungskatalog "(Tat)Orte"} (pp. 29-44). Düsseldorf: Kulturforum NRW.\\ \\ 

Müller, R., \& Brockmann, H. (2006). Steigende Zahl der Krankenhausfälle mit Diagnose "psychische Störung". In R. Müller, \& B. Braun (Eds.), \textit{Vom Querschnitt zum Längsschnitt. Möglichkeiten der Analysen mit GKV-Daten. GEK-Schriftenreihe zur Gesundheitsanalyse}. St. Augustin: Asgard, in press. \\ \\ 

Nanz, P., \& Steffek, J. (2006). Deliberation and democracy in global governance: The role of civil society. In S. Thoyer, \& B. Martimort-Asso (Eds.), \textit{Participation for sustainability in trade} (pp. 61-72). Aldershot: Ashgate.\\ \\ 

Peters, B., Wessler, H., Sifft, S., Wimmel, A., Brüggemann, M., \& Kleinen-von-Königslöw, K. (2006). Die Transnationalisierung von Öffentlichkeiten am Beispiel der Europäischen Union. In S. Leibfried, \& M. Zürn, (Eds.), \textit{Staatlichkeit im Wandel} (pp. 230-261). Frankfurt am Main: Suhrkamp.\\ \\ 

Peters, B., \& Wessler, H. (2006). Die Transnationalisierung von Öffentlichkeiten - analytische Dimensionen, normative Standards, sozialkulturelle Produktionsstrukturen. In K. Imhof, R. Blum, H. Bonfadelli, \& O. Jarren (Eds.), \textit{Demokratie in der Mediengesellschaft} (pp. 125-144). Wiesbaden: VS Verlag.\\ \\ 

Jochum, G., \& Pfaffenberger, W. (2006). Die Zukunft der Stromerzeugung. \textit{Aus Politik und Zeitgeschichte, 13}, 19-26.\\ \\ 

Pfaffenberger, W. (2006). Erneuerbare Energien in Strom-, Gas- und Wärmenetzen. Determinanten der Wirtschaftlichkeit - Heute und Morgen. \textit{VDI Bericht 1929}, 1-14.\\ \\ 

Pfaffenberger, W. (2006). Zu den Fundamentaldaten der Energiepreisentwicklung. \textit{Energiewirtschaftliche Tagesfragen}, Issue 6, 13-16.\\ \\ 

Pfaffenberger, W. (2006). Wertschöpfung und Beschäftigung durch grüne Energieproduktion? \textit{Energiewirtschaftliche Tagesfragen}, Issue 9, 22-26.\\ \\ 

Ress, G. (2006). Würde des Menschen - die gedankliche Herkunft der Menschenrechte und ihre gegenwärtige Funktion. In M. Akyuerek, G. Baumgartner, D. Jahnel, G. Lienbacher, \& H. Stolzlechner (Eds.), \textit{Festschrift Heinz Schaeffer} (pp. 703-715). München: CH Beck. (Gleichzeitig in japanischer Sprache erschienen in den Forschungsannalen der IWAKI-University).\\ \\ 

Ress, G. (2006). Der europäische Gerichtshof für Menschenrechte, seine Reform und die Rolle der nationalen Gerichte (in Japanese). \textit{Journal of Law, Politics and Sociology} Tokyo Keio University, \textit{79}, 77 - 103.\\ \\ 

Ress, G. (2006). Reflections on the protection of property under the European Convention of Human Rights. In L. Wildhaber (Ed.),\textit{ Liber Amicorum}. Basel: Universität Basel, in press.\\ \\ 

Rixen, T. (2006). Die Mühen internationaler Kooperation gegen schädlichen Steuerwettbewerb. In S.A. Schirm (Ed.), \textit{Globalisierung: Forschungsstand und Perspektiven} (pp. 77-98). Baden-Baden: Nomos.\\ \\ 

Rixen, T. (2006). The plight of international cooperation against harmful tax competition. In S.A. Schirm (Ed.), \textit{Globalization. State of the art and perspectives}. London: Routledge, in press.\\ \\ 

Rohlfing, I., Fischer, J., \& Kaiser, A. (2006). The push and pull of ministerial resignations in Germany, 1969-2005. \textit{West European Politics, 29} (4), 709-735. \\ \\ 

Steffek J., \& Kissling, C. (2006). Why co-operate? Civil society participation at the WTO. In C. Joerges, \& E.-U. Petersmann (Eds.), \textit{Constitutionalism, multilevel trade governance and social regulation} (pp. 135-155). Oxford: Hart.\\ \\ 

Uhl, S. (2006). Time for a tea party? Why tax regimes beyond the nation state matter, and why citizens should care. \textit{European Review, 14 }(4), 565-585.\\ \\ 

von Hirschhausen, C., Brunekreeft, G., \& Elmer, C.F. (2006). Recent trends in the privatization and the regulation of network industries - An introduction. \textit{Competition and Regulation in Network Industries, 1}, in press.\\ \\ 

Welzel, C. (2006). Demokratisierung und Demokratisierungswellen. In D. Fuchs, \& E. Roller (Eds.), \textit{Lexikon Politik: Hundert Grundbegriffe} (pp. 25-27). Opladen: Westdeutscher Verlag.\\ \\ 

Welzel, C. (2006). Democratization as an emancipative process: The neglected role of mass motivations. \textit{European Journal of Political Research, 45} (4), 871-896.\\ \\ 

Welzel, C. (2006). Democratization in the human development perspective. \textit{Comparative Sociology, 5} (2-3), 259-290.\\ \\ 

Welzel, C., \& Inglehart, R. (2006), The Human Development Model of Democracy: East Asia in Perspective. In R.J. Dalton, \& D.C. Shin (Eds.), \textit{Citizens, Democracy, and Markets around the Pacific Rim} (pp. 21-49). Oxford: Oxford University Press.\\ \\ 

Welzel, C., \& Inglehart, R. (2006). Emancipative values and democracy: Response to Hadenius and Teorell. \textit{Studies in Comparative International Development, 41} (3), 74-94.\\ \\ 

Werner, W. (2006). The European Social Model: Cause of, or solution to, the present crisis of the European Union? Intereconomics: \textit{Review of European Economic Policy, 1/2} (41), 4-14.\\ \\ 

Werner, W. (2006). Social Policy in the European Union. A View from Germany. \textit{Comparative Economic \& Social Systems}, 3, 39-48.\\ \\ 

Werner, W. (2006). Vom Modell zum Auslaufmodell. Sozialstaat Bundesrepublik Deutschland verliert Vorbildfunktion in Europa. \textit{Vierteljahrschrift für Sozial- und Wirtschaftsgeschichte (VSWG) 4}/92 (2006), in press.\\ \\ 

Werner, W., \& Werner, W. (2006). WTO-Dienstleistungsverhandlungen. Stärkung des plurilateralen Ansatzes. Wirtschaftsdienst, \textit{Zeitschrift für Wirtschaftspolitik, 86} (5), 317-322.\\ \\ 

Werner, W. (2006). Hurricane Betsy and the malfunctioning of the London reinsurance market: An analysis of transatlantic reinsurance trade, 1949-1989. \textit{Financial History Review}, in press.\\ \\ 

Wessler, H., \& Schultz, T. (2006). Can the Mass Media Deliberate? Insights from Print Media and Political Talk Shows. In R. Butsch (Ed.), \textit{Media and Public Spheres} (pp. 15-27). Basingstoke: Palgrave Macmillan.\\ \\ 

