\subsection{Prof. Dr. Dr. Dr. h.c. mult. Georg Ress}

\vspace{0.3cm}
\textbf{Main Research Interests}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	International Law
\item[$\bullet$]	Human Rights
\item[$\bullet$]	European Community Law (Conflicting Fundamental Rights, International Treaties)
\end{enumerate}


\vspace{0.6cm}
\textbf{Research Activities}\\[-0.25cm]

Georg Ress works predominantly of four particular law questions: First, the \textit{Interpretation of Art. 53 ECHR} and the so-called "Drittwirkung" of fundamental rights (since the judgment in the case Caroline von Hannover v. Germany the question has been asked, whether the EurCtHR should not leave a broader sphere of decision for the Constracting States , e.g.; balance between protection of privacy and freedom of press),. Georg Ress' research is concerned with the consequences of such an approach. Second, the \textit{Protection of Property} question of whether the restitution of property which was confiscated after the second world war under communist and socialist regimes are to be considered as a "special category." Third, the so-called \textit{Secret Treaties} collection of undisclosed international treaties, their legal effect and their observance compared with other treaties. And fourth, Diplomatic protection, encompassing a revision of lectures, given 2001 at the Academy of International Law in the Hague (in French). The last project which will take at least six months. Furthermore Georg Ress is working on an article about the interpretation of Art. 5, § 3 ECHR; conditions of release pending a trial.


\vspace{0.6cm}
\textbf{Other Professional Activities}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Legal opinion for the Senate of Bremen on the financial claim against the Federation and other Länder (financial emergency situation)
\item[$\bullet$]	Guest professor at the University of Kyoto
\item[$\bullet$]	Participation in the Conference on the European Internal Market concept, Vienna (Wien), president of one of the sessions
\item[$\bullet$]	Participation in several meetings of the former third section of the European Court of Human Rights, as its president, and of the Grand Chamber
\item[$\bullet$]	Participation in a meeting of the Commission on State Immunity and Human Rights of the Institute of International Law, London
\item[$\bullet$]	Invited expert: Bundestagsanhörung, Menschenrechtsausschuss
\item[$\bullet$]	Participation in a meeting of the Reuters Founders Nomination Committee (member on behalf of the Council of Europe) in London
\item[$\bullet$]  Member of the Supervisory Board of the Saarbr\"ucker Zeitung Verlag und Druckerei GmbH
\end{enumerate}