\section{Selected Knowledge Transfer Activities} \shorttitle{Selected Knowledge Transfer Activities}

\begin{itemize}

\item Executive Teaching for AutoUni in Wolfsburg by K. Schömann.

\item Executive Teaching for Schneider Electric, ThyssenKrupp AG, Volkswagen AG, by C. Stamov Roßnagel.

\item Developing Executive Teaching Program for \textit{Next Generation Leadership Programme} in collaboration with TiasNimbas Business School (Tilburg, NL) by C. Stamov Roßnagel, Course-Director.

\item Executive Teaching for Leadership Academy, Lower Saxony Penitentiary Service, German Society for Personnel Management (DGFP) by C. Stamov Roßnagel.

\item Consulting Project (PI: K. Schömann): Evaluation of company-wide occupational health and safety trainings ENO/RNO Bremen.
ADECCO Institute (PI: K. Schömann and C. Rossnagel): Compendium on Lifelong Learning - Qualification Needs in the OECD - Analysis, Implementation and Policy Recommendations.

\item WISE Demographie Netzwerk (Companies: Deutsche Bahn, Deutsche Bank, EnBW, Lonza, Otto Group, VW) (PIs: S. Voelpel, C. Stamov Roßnagel), (2007-2010).

\item Projekt Innovationsmanagement (Companies: EADS Astrium, KAEFER, Meyer Werft, Rheinmetall) (PI: S. Voelpel), (2007). 

\item Consulting Project (PI: C. Stamov Roßnagel): \textit{An age-differentiated view on work and learning motivation at HeidelbergCement}. HeidelbergCement.

\item Consulting Project (PI: M. Schulz, C. Stamov Roßnagel):\textit{ Evaluation of a learning competency training}. EnBW.

\end{itemize}