\shorttitle{Information and Communication Technologies}
\section{Information and Communication Technologies}

The increasing impact of information and communication technology dominates our everyday
life, our society, and the environment.  Examples comprise the World-Wide-Web, the
ubiquitous use of computers, cellular multimedia and wireless communications, robots in
factories as well as in offices and homes, and sophisticated computer models used to
predict the evolution of complex systems such as the global climate.

The enormous level of integration in micro-electronics has enabled unprecedented progress
in many sectors -- and even more importantly, it has created many new profitable
technologies and services based on them. The 21st century will witness technologies that
enable machines to do things that have been so far restricted to humans: machines will be
able to sense, act, speak, listen, decide and sometimes understand. Our T-shirts may have
their own Internet addresses and wirelessly tell the laundry machine about proper
treatment. We will see cars that negotiate with each other in order to maximize traffic
flow while reducing pollution using sophisticated energy management systems. Manufacturing
technologies will improve using a combination of detectors and software to control
processes. Robots are also more and more used in domains where some autonomy and
intelligence is necessary. They work under conditions where it is unpleasant or even risky
for humans like in abandoned mines or at disaster sites and where they have to deal with
situations unforeseen by their designers and programmers. The hallmark of such smart
systems is their integration of technologies from analogue devices and sensors,
communication systems and networks, internet services, artificial intelligence, machine
learning, robotics, and many more.

The School of Engineering and Science actively contributes to this
rapidly growing, boldly interdisciplinary endeavor, focusing on the
areas described in the following.
%
%{\em{Mathematical and Symbolic Modeling}\\
%  \item Reasoning and Semantics
%  \item Simulation and Control of Complex Systems
%  \item Machine Learning
%  \end{itemize}
%\item {\em{Communication Networks and Systems}}, in particular:
%  \begin{itemize}
%  \item Wireless and Cellular Communications
%  \item Digital Transmission Methods and Coding
%  \item Networks and Protocols
%  \item Harmonic Analysis applied to communications engineering
%  \end{itemize}
%\item {\em{Robotics and Embedded Systems}}, in particular:
%  \begin{itemize}
%  \item Robotics
%  \item Applied Algorithms
%  \end{itemize}
%\item {\em{Knowledge and Information Management Systems}}, in
%  particular:
%  \begin{itemize}
%  \item Raster Data Services
%  \item Knowledge Management Systems
%  \item Distributed Systems
%  \item Hierarchical Data Representation
%  \end{itemize}
%\item {\em{Microelectronic Devices and Technologies}}, in particular:
%  \begin{itemize}
%  \item Electronic Devices and Nano Photonics
%  \item Microelectronics
%  \end{itemize}
%\item {\em{Digital Signal Processing}}, in particular:
%  \begin{itemize}
%  \item Signal Processing in Communications
%  \item Nonlinear Signal Processing and Control
%  \end{itemize}
%\end{enumerate}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "report"
%%% End:
