\subsection{Prof. Dr. Paul Crowther}


\textbf{Main Research Interests}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	Philosophy of Art and Culture
\item[$\bullet$]	Meaning in the Visual Arts
\item[$\bullet$]  Hegelian and Phenomenological Logic and Metaphysics 
\item[$\bullet$]	Philosophy of Art History
\item[$\bullet$]  Victorian Art
\end{enumerate}


\vspace{0.6cm}
\textbf{Research Activities}\\[-0.25cm]

Paul Crowther has worked on three book projects during 2006. He has completed editing and critically introducing the book by R.K. Elliott, \textit{Aesthetics, Imagination, and the Unity of Experience}, which has meanwhile appeared with the Ashgate publishing house. A second book project was concerned with \textit{Defining Art, Creating the Canon: Artistic Value in an Era of Doubt}. It is being published by Oxford University Press. Paul Crowthers' most recent interest is directed towards the \textit{Phenomenology of the Visual Arts}; this book is under review with Cornell University Press. Furthermore Paul Crowther has co-organized a conference on {\itshape Art and Metaphysics}. The conference addressed both historical and conceptual aspects of the relation between visual art and metaphysics. In it the term "metaphysics" was understood broadly so as to encompass philosophical, religious, and scientific meaning. 
\vspace{0.6cm}


\textbf{Organization of Scientific Conferences}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$]	May 2006\newline
	International University Bremen\newline
  "Art and Metaphysics in the Twentieth Century and Beyond"\newline
	(together with Prof. Dr. Isabel Wünsche \& Prof. Dr. Ursula Frohne, IUB)\newline
  funded by the DFG\newline
  international participants: 75
\end{enumerate}


\vspace{0.6cm}
\textbf{Other Professional Activities}\\[-0.25cm]
\begin{enumerate}
\item[$\bullet$] Visiting Fellow at the Slovene Academy of Arts and Sciences
\end{enumerate}


