\section{Grants 2007/2008} \shorttitle{Grants 2007/2008}

\begin{itemize}

\item Bremen International Graduate School of the Social Sciences \textit{BIGSSS"}, Project in cooperation with the University Bremen and the SHSS (Co-PI: U. M. Staudinger), German Excellence Initiative, DFG, (2008-2011). 

\item BMBF (PI: Staudinger et al.). Joint research project:\textit{ Effects of Matches/Mismatches between Aspects of Human and Social Capital, Corporate Strategy and Work Organization on the Physical and Mental Well-Being of Employees }(2007 - 2010).

\item Emmy Noether Research Group, part I (KU 1401/4-1), part II (KU 1401/4-2), and part III (KU 1401/4-3) funded by the DFG, (PI: B.M. Kudielka) \textit{Stress and burnout - Integration of work psychological and psychobiological research methods for the assessment of differential stress patterns in chronic work stress }(2004 - 2009).

\item IRTG International Research Training Group ('Internationales Graduiertenkolleg') of Trier (Germany) and Leiden (The Netherlands) (GRH 1389/1); funded by the DFG (B.M. Kudielka was one out of 11 Co-Applicants (German part)) \textit{Psychoneuroendocrinology of stress: from molecules and genes to affect and cognition} (2006 - 2010).

\item Leopoldina (PI: U. M. Staudinger) \textit{Joint Academy Group: Aging in Germany}(2006-2009).

\item Robert Bosch Foundation (PIs: C. Voelcker-Rehage, B. Godde, U. M. Staudinger): \textit{Old Age on the Move} (2006-2009).

\item Volkswagen Foundation (PIs: B. Godde, K. Schömann, U. M. Staudinger) \textit{Job Mobility and Developmental Outcomes} (2008-2011).

\item Volkswagen Foundation (PI: C. Stamov Roßnagel): \textit{Older workers' cognitive innovation resources} (2008-2011).

\item Volkswagen Foundation Initiative "Gesellschaftliche und kulturelle Herausforderungen Innovationsprozesse in Wirtschaft und Gesellschaft" (PIs: S. Voelpel and G. Van der Vegt): Proposal: \textit{The Effects of the Aging Workforce on the Innovation Process: A Large-Scale Study of Technology Intensive Companies} (2007-2010).

\end{itemize}