\section{PhD Degrees} \shorttitle{PhD Degrees}
\paragraph{}
\begin{flushleft}
\textbf{2007}
\end{flushleft}

\textbf{Otto, Siegmar - with distinction:} "Meaning and Use of the Terms 'Sustainability' and 'sustainable Development'- an empirical study".  


Dissertation Committee: Prof. Dr. Clemens Schwender (Supervisor, Jacobs-University), Prof. Dr. Sven Voelpel (Jacobs University), Prof. Dr. Alfons Matheis (FH Trier), Prof. Dr. Werner Schulz (University of Hohenheim).

\paragraph{}
\begin{flushleft}
\textbf{2008}
\end{flushleft}
\textbf{Fasang, Anette - with distinction:} "Family Biographies and Retirement Processes - A comparative analysis of West Germany and the United Kingdom".


Dissertation Committee: Prof. Dr. Klaus Schömann (Supervisor, Jacobs-University), Prof. Dr. Hilke Brockmann (Jacobs University), Prof. Dr. Karl-Ulrich Mayer (Yale University), Prof. Dr. Silke Aisenbrey (Yeshiva University).
$$ $$
\textbf{Mühlig Versen, Andrea:} "Personality Development in Old Age- A Quasi-Experimental, Longitudinal Field Study".


Dissertation Committee: Prof. Dr. Ursula M. Staudinger (Supervisor, Jacobs University), Prof. Dr. Margit Schreier (Jacobs University), Prof. Dr. Hans-Werner Wahl (University of Heidelberg).
$$ $$
\textbf{Streb, Christoph: }"Empirical Research on Aging Workforce Management: Secondary Data, Grounded Theory, and Case Study Findings with Particular Consideration of the Automobile Industry"'. 


Dissertation Committee: Prof. Dr. Sven Voelpel (Supervisor, Jacobs University), Prof. Dr. Marius Leibold (Stellenbosch University), Prof. Dr. Adalbert FX Wilhelm (Jacobs University), Prof. Dr. Horst-Erich Rikeit (University of Bremen).