\section{Visiting Scholars at the Jacobs Center} \shorttitle{Visiting Scholars at the Jacobs Center}


$$ $$
\textit{Prof. Dr. Nicola Baumann} (Department of Psychology, University of Trier, Presentation: "How do we grow? Personal growth through affect regulation").
$$ $$
\textit{Prof. Dr. Hans-Peter Blossfeld} (Holds the Chair of Sociology I and is the Director of the \href{http://www.ifb.bayern.de/}{Staatsinstitut für Familienforschung at Bamberg University}).
$$ $$
\textit{Prof. Dr. Andreas Diekmann} (Professor of Sociology, ETH Zurich, Presentation: 'Social Cooperation, Results from Experimental Game Theory').
$$ $$
\textit{Dr. Werner Eichhorst} (Institute for the Study of Labor (IZA), Bonn, Presentation: 'From Transfers to Training').
$$ $$
\textit{Prof. Dr. Michael Falkenstein} (Leiter der Projektgruppe "Altern und ZNS-Veränderungen", Institut für Arbeitsphysiologie (IfADo), Technische Universität Dortmund).
$$ $$
\textit{Denis Gerstorf, Ph.D.} (Assistant Professor of Human Development at the Department of Human Development and Family Studies, The Pennsylvania State University, State College (Held a lecture in July at Jacobs Center)).
$$ $$
\textit{Dr. Daniel Grühn} (FPSE-Psychology, University of Geneva, Presentation: 'The Positive and the Negative Side of Older Adults' Memory: Age-Related Differences in Remembering Emotional Information').
$$ $$
\textit{Prof. Dr. Thomas M. Hess }(Department of Psychology, North Carolina State University, NC, USA, Presentation: 'A Social Cognitive Approach to Understanding Aging and Decision Making: Affective, Motivational, and Experiential Influences').
$$ $$
\textit{Prof. Dr. Herbert Heuer }(Leibniz Research Center for Working Environment and Human Factors, Institute for work physiology, University of Dortmund, Presentation: 'Adaptation to Visuo-motor Rotations of Different Magnitude in Younger and Older Adults').
$$ $$
\textit{Prof. Dr. Johannes Huinink }(Professor für Soziologie mit Schwerpunkt "Theorie und Empirie der Sozialstruktur" am Institut für empirische und angewandte Soziologie der Universität Bremen).
$$ $$
\textit{Prof. Dr. Michael Hüther} (Honorary Professor at the European Business School, Director, Institut der deutschen Wirtschaft Köln, Presentation: 'Intergenerational Justice and Economic Growth - A Challenge for Economic Policy').
$$ $$
\textit{Prof. Dr. Jürgen Kocka }(Chair for the History of the Industrial World at the Free University of Berlin, Presentation: 'Chances and Challenges of Aging Societies').
$$ $$
\textit{Prof. Dr. Gisela Labouvie-Vief }(Professor of Social-Emotional Development, University of Geneva, Switzerland, Presentation: 'Dynamic Emotion-Cognition Relations in Adulthood').
$$ $$
\textit{Prof. Dr. Marius Leibold }(Department of Business Management, Stellenbosch University, South Africa).
$$ $$
\textit{Prof. Dr. Pawel Lewicki} (Professor of Psychology, Psychology Department, University of Tulsa). 
$$ $$
\textit{Dr. Dr. Talat Mahmood} (Social Science Research Center Berlin (WZB); Berlin, Germany).
$$ $$
\textit{Prof. Dr. Karl Ulrich Mayer} (Professor of Sociology and Director of the \href{http://www.yale.edu/ciqle/}{Center for Research on Inequalities and the Life Course} (CIQLE) at Yale University, Presentation: 'New Directions in Life Course Research').
$$ $$
\textit{Prof. Dr. Franz J. Neyer} (Professor of Lifespan Development, University of Vechta, Presentation: 'Personality Development and Relationship Development').
$$ $$
\textit{Prof. Dr. Lars Nyberg} (Professor of Neuroscience, Ume? University, Sweden, Presentation: 'Memory and Executive Deficits in Relation to Fronto-Striatal Functioning').  
$$ $$
\textit{Prof. Dr. Ernst Poeppel} (Vorstand des Instituts für Medizinische Psychologie (IMP) der LMU München. Geschäftsführender Vorstand des Humanwissenschaftlichen Zentrums (HWZ) der LMU München; Institute of Medical Psychology, LMU Munich, Presentation: 'Fifty years and beyond: Too old to learn something new?').
$$ $$
\textit{Nilam Ram, Ph.D.} (Assistant Professor, Department of Human Development and Family Studies, The Pennsylvania State University, (Held a lecture in July at Jacobs Center)).
$$ $$
\textit{Prof. Dr. Patricia Reuter-Lorenz} (Professor of Psychology, University of Michigan, Ann Arbor, Presentation: 'Neuro-cognitive Aging and the Compensation Hypothesis').
$$ $$
\textit{Prof. Dr. Ramón Rico} (Department of Social Psychology and Methodology, Faculty of Psychology, Universidad Autónoma de Madrid). 
$$ $$
\textit{Prof. Dr. Klaus Rothermund }(Chair of General Psychology, Institut für Psychologie, Friedrich-Schiller-Universität Jena).
$$ $$
\textit{Prof. Dr. Georg Schreyögg} (Professor of Organization and Leadership, Free University of Berlin, Presentation: 'Characteristics and Relevance of Knowledge-Intensive Firms').
$$ $$
\textit{Dr. Antje Stange} (Visiting Scientist, Adult Development Lab, Georgia Institute of Technology, School of Psychology, Atlanta, Presentation: 'Explaining Others' Behavior: When do Old and Younger People differ in their Social Judgments?').
$$ $$
\textit{Prof. Dr. Jürgen Wegge }(Professor of Industrial and Organizational Psychology, Technical University of Dresden, Presentation: 'The Aging Workforce: Problems and Chances with Respect to Effective Team Work').
$$ $$
\textit{Prof. Dr. Reinhold Weiß} (Deputy President and Head of Research of the Federal Institute for Vocational Education and Training (BIBB), Presentation: 'From Formal Training to a New Learning Culture: Trends and Challenges of Lifelong Learning').it{Prof. Dr. Sherry L. Willis} (Professor of Human Development, Pennsylvania State University, Presentation: 'Midlife: Risks and Resources').
$$ $$
\textit{Prof. Dr. Sherry L. Willis} (Professor of Human Development, Pennsylvania State University, Presentation: 'Midlife: Risks and Resources').
$$ $$
\textit{Dr. Gerben S. Van der Vegt }(Professor of Work and Organizational Psychology, Department of Management and Organization, University of Groningen, NL , Presentation: 'When and Why does Power Asymmetry Affect Team Performance?').
$$ $$
\textit{Prof. Dr. James W. Vaupel} (Director, Max Planck International Research Network on Aging, Professor of Demography, Max Planck Institute for Demographic Research, Rostock, Presentation: 'Remarkable Plasticity of Longevity - Policy Challenge of Population Aging').
