@Article{Nau1,
  author =   {Bakirci, H., Nau, W.M.,},
  title =    {Fluorescence Regeneration as Signaling Principle for Choline and Carnitine Binding:
  A Refined Supramolecular Sensor System Based on a Fluorescent Azoalkane},
  journal =      {Adv. Funct. Mat.},
  year =     {2006},
  volume =    {16},
  pages =     {237-242}
}
@Article{Nau2,
  author =   {Pischel, U., Patra, D., Koner A.L., Nau, W.M.,},
  title =    {Investigation of Polar and Stereoelectronic Effects on Pure Excited-Sate Hydrogen
  Atom Abstractions from Phenols and Alkylbenzenes},
  journal =      {Photochem. Photobiol.},
  year =     {2006},
  volume =    {82},
  pages =     {310-317}
}

@Article{Nau3,
  author =   {Mohanty, J., Bhasikuttan, A.C., Nau, W.M., Pal, H.},
  title =    {Host-Guest Complexation of Neutral Red with Macrocyclic Host Molecules:
  Contrasting pK_a Shifts and Binding Affinities for Cucurbit[8]uril and \beta-Cyclodextrin},
  journal =      {J. Phys. Chem. B},
  year =     {2006},
  volume =    {110},
  pages =     {5132-5138}
}

@Article{Nau4,
  author =   {Vannesj\"{o} Lundgren, C., Koner, A.L., Tinkl, M., Pischel, U., Nau, W.M.},
  title =    {Reaction of Singlet-Excited 2,3-Diazabicyclo[2.2.2]oct-2-ene and \emph{tert}-Butoxyl
  Radicals with Aryl-Substituted Benzofuranones},
  journal =      {J. Org. Chem.},
  year =     {2006},
  volume =    {71},
  pages =     {1977-1983}
}

@Article{Nau5,
  author =   {Hennig, A., Roth, D., Enderle, T., Nau, W.M.},
  title =    {Fast Time-Resolved Fluorescence Protease Assays},
  journal =      {ChemBioChem.},
  year =     {2006},
  volume =    {7},
  pages =     {733-737}
}

@Article{Nau6,
  author =   {Bakirci, H., Schwarzloe, T., Koner, A.L., Nau, W.M.},
  title =    {Analysis of Host-Assisted Guest Protonation Exemplified for
  p-Sulfonatocalix[4]arene - Towards Enzyme-Mimetic pK_a Shifts},
  journal =      {Chem. Eur. J.},
  year =     {2006},
  volume =    {12},
  pages =     {4799-4807}
}

@Article{Nau7,
  author =   {Sahoo, H., Hennig, A., Nau, W.M.},
  title =    {Temperature-Dependent Loop Formation Kinetics in Flexible
  Peptides Studied by Time-Resolved Fluorescence Spectroscopy},
  journal =      {Intern. J. Photoenergy},
  year =     {2006},
  volume =    {8},
  pages =     {89638},
}

@Article{Nau8,
  author =   {Sahoo, H., Roccatani, D., Zacharias, M., Nau, W.M.},
  title =    {Distance Distributions of Short Polypeptides Recovered
  by Fluorescence Resonance Energy Transfer in the 10\AA Domain},
  journal =      {J. Am. Chem. Soc.},
  year =     {2006},
  volume =    {128},
  pages =     {8118-8119}
}

@Article{Nau9,
  author =   {Bakirci, H., Koner, A.L., Dickman, M.H., Kortz, U., Nau, W.M.},
  title =    {Dynamically Self-Assembling Metalloenzyme Models Based on Calixarenes},
  journal =      {Angew. Chem.},
  year =     {2006},
  volume =    {118},
  pages =     {7560-7564}
}



@Unpublished{Nau10,
  author =   {Sahoo, H. and Nau,  W.M.},
  title =    {Phosphorylation-Induced Rigidification of Peptides Probed by Time-Resolved Fluorescence Spectroscopy},
  note =     {Ind. J. Rad. Res. in press},
  year =      {2006}

}

@Unpublished{Nau11,
  author =   {Moorthy, N.J. and Koner, A.L. and Samanta, S. and Singhal, N. and Nau, W.M. and Weiss, R.G.},
  title =    {Diastereomeric Discrimination in the Lifetimes of Norrish Type II Triplet 1,4-Biradicals and
  Stereo-Controlled Partitioning of their Reactivity (Yang Cyclization vs Type II Elmination},
  note =     {Chem. Eur. J.},
  year =      {2006}

}

@Unpublished{Nau12,
  author =   {Koner, A.L. and Nau, W.M.},
  title =    {Cucurbituril Encapsulation of Fluorescent Dyes},
  note =     {Supramol. Chem. 18, in press},
  year =      {2006}

} @Unpublished{Nau13,
  author =   {Hennig, A. and Florea, M. and Roth, D. and Enderle, T. and Nau, W.M.},
  title =    {Design of Peptide Substrates for Nanosecond Time-Resolved Fluorescence Assays of
  Proteases: 2,3-Diazabicycloe[2.2.2]oct-2-ene as a Noninvasive Fluorophore},
  note =     {Anal. Biochem. in press},
  year =      {2006}

}

@Unpublished{Nau14,
  author =   {Mohanty, J. and Pal, H. and Ray, A.K. and Kumar, S. and Nau, W.M.},
  title =    {Supramolecular Dye Laser with Cucurbit[7]uril in Water},
  note =     {ChemPhysChem in press},
  year =      {2006}

}
