
 \newpage
\shorttitle{The School of Engineering and Science}
\section{The School of Engineering and Science}
\subsection{Administration}
\shorttitle{Administration of the School of Engineering and Science}
\begin{tabular}{ll}
Prof. Dr. Kramer, Bernhard &Vice President and Dean \\
 Dr. Allner, Anke
 & Director, Dean's Office \\ Schreiber, Angela  & Assistant to
the Dean \\ Buck, Iris  & Graduate Admission \\
 Dr. Frischholz, Svenja
& Graduate Student Affairs \\
 Knoop, Katja & Team Assistant to the
Faculty \\
 Manss, Sigrid  & Team Assistant to the Faculty \\
 Pankratz, Elke
&Team Assistant to the Faculty
\end{tabular}

\subsection{Advisory Board}
\begin{tabular}{ll}
  Prof. Dr. Andrew S. Douglas (Chair)  & Johns Hopkins University, Baltimore, MD \\
 Prof. Dr. med.
Hans-Jochen Heinze & Otto-von-Guericke-Universität, Magdeburg\\
Prof. Dr. Gotthilf Hempel & Bremen \\
 Prof. Dr. James L. Kinsey & William Marsh Rice University, Houston, TX\\
  Prof. Dr. Berrien Moore
III,  & University of New Hampshire \\ Prof. Dr. Heinz-Otto Peitgen
& MeVis, Bremen \\ Prof. Dr. Klaus Pinkau &München \\ Prof. Dr.
Manfred T. Reetz & Max-Planck-Institut für Kohlenforschung,
Mühlheim/Ruhr \\ Prof. Dr. Karl Wieghardt & Max-Planck-Institut für
Strahlenchemie, Mühlheim/Ruhr \\
\end{tabular}

\shorttitle{Faculty} \subsection{Faculty}
\begin{longtable}{ll}
Antoulas, Athanasios C., Ph.D.&Visiting Professor of Electrical Engineering  \\
Dr. Baier, Stephan& Visiting Lecturer in Mathematics \\
Dr. Bau, Michael& Associate Professor of Geosciences\\
Dr. Baumann, Peter& Associate Professor of Computer Science \\
Dr. Belov, Alexei& Visiting Professor of Mathematics \\
Dr. Bergholz, Werner& Professor of Electrical Engineering \\
Dr. Bijma, Jelle& Adjunct Professor of Marine Geosciences \\
& Alfred Wegener Institute for Polar and Marine Research \\
Dr. Birk, Andreas& Associate Professor of Computer Science  \\
Dr. Bode, Mathias& Lecturer of Electrical Engineering \\
Dr. Boetius, Antje& Associate Professor of Microbiology  \\
Dr. Brix, Klaudia& Professor of Cell Biology \\
Br\"uggen, Marcus, Ph.D.&Associate Professor of Astrophysics \\
Dr. Carpin, Stefano& Assistant Professor of Computer Science \\
Fernàndez-Lahore, Marcelo, Ph.D.&Associate  Professor of Downstream-Processing \\
Dr. Fritz, J\"urgen& Assistant Professor of Biophysics \\
Dr. Gl\"ockner, Frank Oliver& Associate Professor of Bioinformatics  \\
& (joint appointment with the MPI for Marine Microbiology)\\
Haas, Harald, Ph.D.&Associate  Professor of Electrical Engineering \\
Dr. Haerendel, Gerhard& Distinguished Professor of Space Physics\\
Dr. Henkel, Werner& Professor of Electrical Engineering \\
Hilgetag, Claus C.,Ph.D.&Associate Professor of Neuroscience \\
Dr. H\"{u}tt, Marc-Thorsten& Associate Professor of Computational Systems Biology \\
Dr. Jaeger, Herbert& Associate Professor of Computational Science\\
Dr. Jeltsch, Albert& Professor of Biochemistry \\
Dr. Kaimanovich, Vadim& Professor of Mathematics \\
Dr. Khalili, Arzhang& Professor of Computational Science \\
& (joint appointment with the MPI for Marine Microbiology)\\
Dr. Kleinekath\"{o}fer, Ulrich& Associate Professor of Physics \\
Dr. Knipp, Dietmar& Assistant Professor of Electrical Engineering \\
Dr. K\"ohler, Angela& Adjunct Professor of Marine Biology \\
& Alfred Wegener Institute for Polar and Marine Research \\
Dr. Kohlhase, Michael& Professor of Computer Science \\
Kortz, Ulrich, Ph.D.&Associate Professor of Chemistry \\
Dr. Koschinsky-Fritsche, Andrea& Associate Professor of Geosciences \\
Dr. K\"uhl, Nicole& Research Instructor (Biochemistry \& Cell Biology) \\
Dr. Kuhnert, Nikolai& Associate Professor of Chemistry \\
Dr. Lerchl, Alexander& Professor of Biology \\
Dr.-Ing Linsen, Lars& Associate Professor of Computer Science and
Computational Science \\
Dr. L\"{o}we, Astrid& Research Assistant in Physics\\
Dr.-Ing Mahleko, Bendick& University Lecturer of Electrical
Engineering \\
Mallahi-Karai, Keivan, Ph.D.&Visiting Lecturer of Mathematics \\
Dr. Materny, Arnulf&  Professor of Chemical Physics  \\
Dr. Meyer-Ortmanns, Hildegard&  Professor of Physics  \\
Meyer-Rochow, V. Benno, Ph.D., D.Sc. &Professor of Biology  \\
Dr. Muskhelishvili, Georgi& Professor of Genetics \\
Dr. Nau, Werner& Professor of Chemistry \\
Nugent, Thomas, Ph.D.&Assistant Professor of Chemistry  \\
Oliver, Marcel, Ph.D.&Assistant Professor of Mathematics \\
Dr. Oswald, Peter& Professor of Mathematics \\
Dr. Penkov, Ivan& Professor of Mathematics \\
Pfander, G\"otz, Ph.D.&Assistant Professor of Mathematics \\
Richards, Ryan M., Ph.D.&Assistant Professor of Chemistry \\
Dr. Roccatano, Danilo& University Lecturer of Chemistry \\
Dr. Rosswog, Stephan& Assistant Professor of Astrophysics \\
% \end{longtable}
% \newpage
% \begin{longtable}{ll}
Schleicher, Dierk, Ph.D.&Professor of Mathematics  \\
Dr. Sch\"onwälder, J\"urgen& Associate Professor of Computer
Science \\
Schupp, Peter, Ph.D.&Professor of Physics  \\
Dr. Schwaneberg, Ulrich& Associate Professor of Biochemical Engineering \\
Springer, Sebastian, D.Phil. &Assistant Professor of Biochemistry and Cell Biology\\
Dr. Stamerjohanns, Heinrich& Research Assistant, Head of Computer Science Lab \\
Dr. Stoll, Michael& Associate Professor of Mathematics \\
Dr. Styrkas, Konstantin& Visiting Assistant Professor of Mathematics \\
Tautz, Stefan, Ph.D.&Associate Professor of Physics \\
Dr. Thomsen, Laurenz& Professor of Geosciences \\
Dr. Ullrich, Matthias& Professor of Microbiology \\
Unnithan, Vikram, Ph.D.&Assistant Professor of Geoscience \\
Dr. Vogt, Joachim& Associate Professor of Physics \\
Dr. Wagner, Veit&  Associate Professor of Physics \\
Wallace, Jon, Ph.D.&Assistant Professor of Electrical Engineering \\
Wells, Raymond O., Ph.D.&Distinguished Professor of Mathematics  \\
Dr. Welte, Dietrich& Adjunct Professor of Geosciences \\
Dr. Wiltshire, Karen Helen& Professor of Geoscience \\
Dr. Winterhalter, Mathias& Professor of Biophysics  \\
Dr. Zacharias, Martin& Associate Professor of Computational Biology \\
Zupanc, G\"unther K. H.,Ph.D.&Professor of Neurobiology       \\

\end{longtable}

\shorttitle{Staff} \subsection{Staff}
\begin{longtable}{ll}
Abu-Alhiga, Rami & Integrated PhD Student (Electrical Engineering)\\
Afgani, Mostafa & Research Associate (Electrical Engineering) \\
Al-Buloshi, Mohammed & Graduate Student (Biochemical Engineering)\\
Al-Karablieh, Nehaya & Graduate Student (Microbiology)\\
Al-Shbat, Shering & Integrated PhD Student (Computer Science)\\
Alexander, Brian & Graduate Student (Geology/Geochemistry)\\
%Dr. Allner, Anke-Maria & Director, Dean's Office \\
Bakirci, Huseyin & Graduate Student (Chemistry)\\
Dr. Balster, Torsten & Research Associate\\
Bassil, Bassem & Graduate Student (Nanomolecular Science)\\
Becker, Sandra & Lab Assistant (Biology)\\
Behnke, Torsten & Technician, Ocean Lab\\
Benor, Amare & Graduate Student (Electrical Engineering)\\
Berger, Michael & Graduate Student (Biochemistry)\\
Bharucha, Zubin & Integrated PhD Student (Electrical Engineering) \\
Binner, Sabine & Research Assistant (Biochemical Engineering)\\
Blanusa, Milan & Graduate Student (Biochemical Engineering)\\
Dr. Blohmann, Christian & Postdoctoral Fellow (Physics)\\
Borchert, Britta & Graduate Student (Biochemistry)\\
Braun, Yvonne & Research Associate/Graduate Student (Microbiology)\\
B\"{u}th, Heiko & Graduate Student (Cell Biology)\\
Burau, Claudia & Lab Assistant (Biochemistry)\\
Caballero Hern\'{a}ndez, Josefa & Graduate Student (Biochemical Engineering)\\
Cabrera, Rosa & Postdoctoral Fellow (Downstream Processing) \\
Chahar, Sanjay & Graduate Student (Biochemistry)\\
Chan, Kah-Yoong & Graduate Student (Electrical Engineering)\\
%                    \end{longtable}
%                   \newpage
%                   \begin{longtable}{ll}
Chonnaparamutt, Winai & Graduate Student (Computer Science)\\
Chubarova, Elena, Ph.D. & Postdoctoral Fellow (Chemistry) \\
Claus, Ute & Lab Assistant (Biochemistry) \\
Curusku, Jeremy & Research Associate (Computational Biology) \\
Dairpoosh, Farnoosh& Graduate Student (Biochemical Engineering) \\
Dammann, Frauke & IMO Assistant (Mathematics)\\
Dan, Marius & Graduate Student (Astrophysics) \\
de Jesus Mendes, Pedro Andr\'{e} & Graduate Student (Geosciences)\\
Dr. Dehnert, Manuel& Postdoctoral Fellow (Computational Systems Biology) \\
Dhayalan, Arunkumar & Graduate Student (Biochemistry)\\
Dickman, Michael, Ph.D. & Senior Research Associate (Chemistry)\\
Dinkel, Thomas & Graduate Student (Electrical Engineering) \\
Donfack, Patrice & Graduate Student (Chemical Physics) \\
Donnelly, Stephen & Postdoctoral Fellow (Mathematics) \\
Dunkhorst, Anna & Graduate Student (Cell Biology) \\
Ehlers, Birte-Marie & Graduate Student (Geosciences)\\
El-Sheshtawy, Hamdy & Graduate Student (Chemistry) \\
Elgala, Hany & Lab Assistant (Electrical Engineering) \\
%Dr. Frischholz, Svenja & Assistant (Administration Graduate Students)\\
Felden, Janine & Graduate Student (Marmic) \\
Fu, Yanzhe & Graduate Student (Geosciences) \\
Gama Saldago, Antonio & Research Associate (Neurobiology) \\
Garcia Gutierrez, Angelica & Graduate Student (Computer Science) \\
Garcia-Novoa, Rosa & Graduate Student (GeoOcean Dynamics)\\
Garstka, Malgorzata & Graduate Student (Biochemistry)\\
Gburek, Benedikt & Research Associate and Graduate Student (Physics) \\
Geberth, Daniel & Graduate Student (Computational Systems Biology) \\
Geertz, Marcel & Graduate Student (Biochemistry)\\
Dr. Gelessus, Achim & CLAMV Server Manager\\
Ghimire, Birendra & Graduate Student (Electrical Engineering) \\
Gobet, Angelique & Graduate Student (Marmic)\\
Ghosh, Abhijit & Graduate Student (Chemistry)\\
Grote, Karen & Technical Assistant (Biology)\\
Guimbretiere, Thomas & Graduate Student (Astrophysics) \\
Hanelt, Sharifah Nora & Research Associate (Geosciences) \\
Hassan, Khaled & Research Associate (Electrical Engineering)\\
Hassanin, Rasha & Graduate Student (Chemical Physics) \\
Hauschildt, Jakob & Graduate Student (Geophysics)\\
Dr. Helling, Robert & Research Associate (Physics)\\
Hennig, Andreas & Graduate Student (Chemistry) \\
Dr. Henze, Stina & Research Associate (Physics)\\
Hinsch, Karen & Graduate Student (Neuroscience)\\
Dr. Hoeft, Matthias & Postdoctoral Fellow (Astrophysics)\\
Hofbauer, Michael & Electronic Technician (Ocean Lab)\\
Holzapfel, Christine & Lab Assistant Chemistry\\
Hoppe, Arne & Graduate Student (Physics)\\
Hu, Fangning & Graduate Student (Electrical Engineering)\\
Dr. Hu, Jun-Cheng & Postdoctoral Fellow (Chemistry) \\
Hussain, Firasat & Graduate Student (Chemistry)\\
Ihle, Saskia & Graduate Student (Biochemical Engineering)\\
Ismail, Amal & Graduate Student (Chemistry)\\
Ivanovska, Tetyana & Graduate Student (Computer Science)\\
Jordans, Silvia & Graduate Student (Cell Biology)\\
Josuttis, Daniela & Lab Technician (Biochemical Engineering)\\
Jurkowski, Renata & Graduate Student and Research Associate (Biochemistry)\\
Jurkowski, Thomasz & Graduate Student (Biochemistry)\\
Kaffl, Alexandra & Graduate Student (Mathematics)\\
von der Kammer, Bernd& Lab Assistant Physics \\
Kannan, Srinivasaraghavan & Research Associate (Biology) \\
Dr. Karpen, Volker & Research Associate (Oceanography)\\
%\end{longtable} \newpage
%\begin{longtable}{ll}
Keithahn, Christian & Graduate Student (Biology)\\
Klepsch, Meike & Lab Assistant (Biochemistry and Cell Biology) \\
Klose, Melanie & Graduate Student (Biology) \\
%Knoop, Katja& Team Assistant to the Faculty \\
Kohlhase, Andrea & Guest (Computer Science)\\
Kolyuzhov, Dennis & Graduate Student (Electrical Engineering)\\
Konradi, Jakow & Graduate Student (Physics)\\
Kottmann, Renzo & Graduate Student (Marine Microbiology)\\
Kraynov, Alexander & Graduate Student (Chemistry)\\
Kronenberger, Astrid & Graduate Student (Physics)\\
Kurtev, Stoyan & Graduate Student (Neuroscience)\\
Dr. Laser, Heike & Postdoctoral Fellow (Biology)\\
Laskowski, Katja & Lab Assistant (Biochemistry \& Cell Biology)\\
Lau, Tin Fan Stanley & Graduate Student (Biology)\\
Laubner, Bastian & Integrated PhD Student (Mathematics) \\
Liebert, Kirsten & Research Associate, Graduate Student (Biochemistry)\\
Limmanee, Apirath & Graduate Student (Electrical Engineering)\\
Lindemann, Marcus & Graduate Student (Biochemical Engineering)\\
Dr. Linnenberg, Susanne & Research Assistant (Teaching Lab Physics)\\
Linow, Marina & Research Associate (Biochemical Engineering)\\
Lucosevicius, Mantas & Graduate Student (Computer Science)\\
Mal, Sibsankar & Graduate Student (Chemistry)\\
%Manss, Sigrid & Team Assistant to the Faculty\\
Marbler, Herwig & Research Associate (Geosciences)\\
Maurer, Sebastian & Graduate Student (Biochemistry)\\
Mavathur, Ramesh & Graduate Student (Biochemistry)\\
Mawick, Jule & Lab Assistant (Geoscience)\\
May, Andreas & Graduate Student (Biochemical Engineering)\\
Mayer, Kristina & Graduate Student (Cell Biology)\\
Mei\ss ner, Daniela & Technical Assistant (Biology)\\
Mesleh, Read & Graduate Student (Electrical Engineering)\\
Mishra, Monalisa & Graduate Student (Biology)\\
Moje, Annika & Lab Assistant (Geoscience) \\
Molchanov, Vladimir  & Graduate Student (Mathematics) \\
Momeu, Iuliana Carmen & Graduate Student (Biochemical Engineering)\\
Mudesir, Abdurazak & Graduate Student (Electrical Engineering)\\
M\"uller, Christine & Graduate Student (Computer Science)\\
M\"uller, Jan Steffen & Graduate Student (Mathematics)\\
M\"uller, Normen & Graduate Student (Computer Science) \\
M\"uller-Linow, Mark & Graduate Student (Computational Systems Biology)\\
Namboodiri, Vinu & Graduate Student (Chemical Physics)\\
Nazor, Jovanna & Graduate Student (Biochemical Engineering) \\
Neu, Florian & IRCCM/CLAMV Systems Administrator\\
Nour Abdel-Gawad Ahmed, Mohammed & Graduate Student (Computer Science)\\
Normann, Immanuel & Graduate Student (Computer Science)\\
Nsouli, Nadeen & Graduate Student (Chemistry) \\
Dr. Omiyi, Peter & Postdoctoral Fellow (Electrical Engineering)\\
Onaca, Ozana & Graduate Student (Biochemical Engineering)\\
Pagel, Uwe & Electrical Engineering \& Computer Science Technician\\
%Pankratz, Elke & Team Assistant to the Faculty\\
Pathak, Kaustubh, Ph.D. &Postdoctoral Fellow (Computer Science) \\
%                   \end{longtable} \\
%                   \newpage
%                   \begin{longtable}{ll}
Pereira Da Silva Gomes, Joana Filipa & Postdoctoral Fellow (Biophysics)\\
Pezeshki, Soroosh & Graduate Student and Research Associate (Physics)\\
Pfingsthorn, Max & Graduate Student (Computer Science)\\
Piedra-Garza, Luis & Graduate Student (Chemistry)\\
Poppescu, Traian & Graduate Student (Astrophysics)\\
Poppinga, Jann & Graduate Student (Computer Science)\\
Prabhakar, Rajendran & Graduate Student (Nanomolecular Science)\\
Praeg, Daniel, Ph.D. & Research Associate (Geosciences)\\
Prodanovic, Radivoje, Ph.D. & Postdoctoral Fellow (Biochemical Engineering)\\
Purser, Autun & Integrated PhD Student (Geosciences)\\
Qu, Hong & Graduate Student (Cell Biology)\\
Rabe, Florian & Graduate Student (Computer Science)\\
Radicchi, Filippo & Graduate Student (Physics)\\
Dr. Ragozin, Sergey & Postdoctoral Fellow (Biochemistry)\\
Rajendran, Raphael Samuel & Graduate Student (Neurosciences)\\
Dr. Ramaye, Yannic & Postdoctoral Fellow (Biophysics)\\
Rashkov, Peter & Graduate Student (Mathematics)\\
Rathert, Philipp & Graduate Student (Biochemistry)\\
Rehders, Maren & Lab Assistant (Biochemistry and Cell Biology)\\
Reicke, Markus & Lab Assistant (Chemistry)\\
Dr. R\"{o}diger, Elke & Research Associate (Astrophysics)\\
Rohde, Christian & Graduate Student (Biochemistry)\\
Rosenk\"{o}tter, Frank & Lab Assistant (Physics)\\
Rosenthal, Paul & Graduate Student (Computer Science)\\
R\"{u}ckert, Johannes & Graduate Student (Mathematics)\\
Rulli, Matteo & Graduate Student (Physics)\\
Sahoo, Harekrushna & Graduate Student (Chemistry)\\
Santillano, Daniel & Graduate Student (Marmic)\\
Scaria, Abraham & Graduate Student (Physics)\\
Dr.Sch\"{a}fer, Angela & Research Associate (IRCCM)\\
Dr. Schirmer, Thomas & Research Associate (Geosciences)\\
Schlickenrider, Martina & Research Associate (Biochemistry)\\
Schmidt, Katja & Graduate Student (Geoscience)\\
Schneewei{\ss}, Clemens & Research Associate (Biochemistry)\\
%Schreiber, Angela & Assistant to the Dean\\
Schr\"{o}der, Markus & Graduate Student and Research Associate (Physics)\\
Schwarzlose, Thomas & Research Assistant, Teaching Lab Chemistry\\
Dr. Schwarzpaul, Kristin & Research Associate (Biology)\\
Schwerdtfeger, Maike & Lab Assistant Biochemistry \\
Schwertfeger, S\"{o}ren & Graduate Student (Computer Science)\\
Shaik, Mona & Visiting Graduate Student (Electrical Engineering)\\
Sieker, Florian & Graduate Student (Bioinformatics)\\
Sharma, Praseh & Graduate Student (Geosciences)\\
Simon, Tatjana & Technical Assistant (Biology)\\
Dr. Solodukhin, Sergey N. & Senior Research Associate (Physics)\\
Dr. Sommer, Angela & Research Associate (Biology)\\
Dr. Soubatch, Serguei & Research Associate (Physics)\\
Sourly-Gopala, Divakara & Graduate Student (Chemistry)\\
Srivastava, Abhishek & Graduate Student (BioRec)\\
Stroehlein, Thomas & Animal Keeper\\
Suchopar, Andreas & Lab Assistant Chemistry \\
Tayakuniyil, Praveen & Graduate Student (Biochemistry)\\
Tee, Kang Lan & Graduate Student (Biochemical Engineering)\\
Temirov, Ruslan & Graduate Student (Nanomolecular Science)\\
Thomsen, Claudia & Research Associate (Oceanography) \\
% \end{longtable}
%                   \newpage
%                   \begin{longtable}{ll}
Thon, Michael & Graduate Student (Mathematics)\\
T\"{o}mmers, Stephanie & Graduate Student (Biochemical Engineering)\\
Tran, Ha Manh & Graduate Student (Computer Science)\\
Tran, Que-Tien & Graduate Student (Biophysics)\\
Tran, Van Long & Graduate Student (Computer Science)\\
Vennapusa, RamiReddy & Graduate Student (Biochemical Engineering)\\
Venkatraman, Hrishikesh & Graduate Student (Electrical Engineering)\\
Vilone, Daniele, Ph.D. & Postdoctoral Fellow (Physics)\\
Viergutz, Thomas & Marine Technology Engineer\\
von Deetzen, Neele & Graduate Student (Electrical Engineering)\\
Wagner, Hannes & Graduate Student (Geosciences)\\
Wakchaure, Vijay & Graduate Student (Chemistry)\\
Wecker, Patricia & Graduate Student (Microbiology)\\
Wellbrock, Ursula & Research Assistant (Biology)\\
Wensing, Annette & Graduate Student (Microbiology)\\
Wong, Tuck Seng & Graduate Student (Biochemical Engineering)\\
Wolters, Brit & Graduate Student (Cell Biology)\\
W\"{u}rdemann, Chris Andr\'{e} & Graduate Student (Genetics)\\
Yaneva, Rakina & Graduate Student (Cell Biology)\\
Yang, Mouyu & Graduate Student (Biology)\\
You, JiangJiang & Graduate Student (Astrophysics)\\
Dr. Yu, Jin & Postdoctoral Fellow (Neuroscience)\\
Zhang, YingYing & Graduate Student (Biochemistry)\\
Zhao, Mingjie, Ph.D. & Postdoctoral Fellow (Electrical Engineering)\\
Zhu, Ziwei & Graduate Student (Biochemical Engineering)\\
Dr. Zieger, Bertalan & Postdoctoral Fellow (Physics)\\
Dr. Zieger, Marina & Postdoctoral Fellow (Biology)\\
Dr. Zupanc, Marianne & Research Associate (Neurobiology)\\
%
%                      \end{longtable}
%                  \newpage
%\begin{longtable}{ll}

\end{longtable}
%\end{center}

\newpage
\shorttitle{ICTS Guests} \subsection{ICTS Guests} \label{ICTS}



\begin{longtable}{ll}
  Professor Dr.~Roland Benz &   Universit\"at
W\"urzburg, Germany
\\
Professor Dr.~Jan Bergstra&  University of Amsterdam, The Netherlands\\
Dr.~Andrey Bessonov& University of Sankt Petersburg, Russia\\
Dr.~S.M. Bezrukov&  National Institute of Health, Bethesda, USA\\
Dr. Georges Bouzerar&   Laboratoire Louis Nel, Grenoble, France\\
Dr. Henk Bruin&  University of Surrey, UK\\
Professor Dr.~Mark Burgess& University College Oslo, Norway\\
Professor Dr.~Val\'erie Cabuil&     Universit\'e Pierre et Marie
Curie, Paris, France\\
Dr.~Fabio Cavaliere& Universit\'a di Genova, Italy \\ Professor
Dr.~Shengbo Chen&      Institute of Geography and Natural
Resources, Beijing, PR China\\
Elizabeth Dan-Cohen&     University of California, Berkeley, USA\\
Professor Dr.~Gero Decher&      Institut Charles Sadron, Strasbourg,
France\\
Dr.~Martin Evans&        University of Edinburgh, UK\\
Dr.~Tom Fisher&      University of Cambridge, UK\\
Dr.~Claus F\"utterer&       Institut Marie Curie, Paris, France\\
Professor Dr.~Mariano Grasselli&     Universidad Nacional de
Quilmes,
Argentina\\
Dr.~Giovanni Indiveri&       University of Lecce, Italy\\
Professor Dr.~Dieter J\"ager&      Emory University, Atlanta, USA\\
Professor Dr.~Larry S. Liebovich&        Florida Atlantic
University,
USA\\
Professor Liviu Movileanu&      Syrakuse University, USA\\
Dr.~Sergei Nechaeev&     CNRS Orsay, France\\
Professor Dr.~Catherine O'Neill&     Columbia University, USA\\
Dr.~Marieke Postma&     NIKHEF, Amsterdam, The Netherlands\\
Dr.~Enrico Ramirez-Ruiz&    Institute of Advanced Studies,
Princeton, USA\\
Professor Dr.~Helmut Ringsdorf&      Universit\"at Mainz, Germany\\
Dr.~Karin R\"omisch&       University of Cambridge, UK\\
Lucile Sassatelli&       ENSEA-ETIS, Cergy-Pontoise, France\\
Professor Dr.~J\"urgen Schnack&        Universit\"at Osnabr\"uck,
Germany\\
Professor Dr.~Gerhard Schwarz&       Biozentrum Basel, Switzerland\\
Professor Dr.~Vera Serganova&       University of California,
Berkeley, USA\\
Professor Dr.~Nobuo Shimamoto&     National Institute of Genetics,
Mishima, Japan\\
Professor Dr.~Canan Tari&        Izmir Institute of Technology,
Turkey\\
Professor Dr.~Alexander Tikhomirov&  Yaroslavl State Pedagogical
University, Russia\\
Dr.~Andrew Travers&      Medical Research Council, Cambridge, UK\\
Dr.~Martin Weigt&        ISI Foundation, Torino, Italy\\
Professor Dr.~James Whisstock&      Monash University, Victoria,
Australia\\
Dr.~Wojtek Zakrzewski&   University of Durham, UK\\
Dr.~Michael Zaks&    Humboldt-Universit\"at Berlin, Germany\\
Professor Dr.~Gregg Zuckerman&   Yale University, USA.
\end{longtable}
