
\section{Education}
The School of Engineering and Science offers 12 Bachelor of Science
programs

\begin{myitemize}
\item Mathematics
\item Physics
\item Chemistry
\item Biology

\item Biochemical Engineering
\item Biochemistry and Cell Biology
\item Bioinformatics and Computational Biology
\item Geosciences and Astrophysics
\item Computer Science
\item Electrical and Computer engineering
\item Electrical Engineering and Computer Science
\end{myitemize}
\ \ \\
 and seven Master's programs
\ \ \\
\begin{myitemize}
\item Mathematical Sciences
\item Astroparticle Physics
\item Biological Recognition
\item Nanomolecular Science
\item Geo-Ocean Dynamics
\item Communications, Systems and Electronics (Electrical
Engineering)
\item Smart Systems (Computer Science.)
\end{myitemize}


\subsection{Master's Degrees}\shorttitle{MSc Degrees}
\paragraph{Biological Recognition}
\begin{enumerate}
    \item {\sl  Esther  Ghanem:}    `` Hetrologous expression of murine tapasin in the yeast expression systems S.cerevisiae and P.pastoris" \\ Examiners:     Prof. Dr. Albert Jeltsch,   Prof. Dr. Sebastian Springer
    \item {\sl  Srinivasaraghavan   Kannan:} ``Enhanced Conformational sampling of peptides and proteins by Biasing potential Replica Exchange Molecular Dynamics Simulations (BP - REMD)" \\ Examiners:     Prof. Dr. Martin Zacharias,   Prof. Dr. Mathias Winterhalter
    \item {\sl  Rustem  Khusainov :}      ``On the facilitation of dye-affinity sorption methods for Downstream Processing of bioproducts" \\ Examiners:     Prof. Dr. Marcelo Fernandez-Lahore  ,   Prof. Dr.Mathias Winterhalter
    \item {\sl  Liliya  Kulishova :}      ``Investigation of the Residues Involved in Target Sequence Recognition by the M.EcoRV Adenine-N6-methyltransferase" \\ Examiners:     Prof. Dr. Albert Jeltsch    ,   Prof. Dr. Ulrich Schwaneberg
    \item {\sl  Benny   Mwale:}    ``Encapsulation and Characterization of Horseradish Peroxidase in Liposomes" \\ Examiners:     Prof. Dr. Mathias Winterhalter,   Prof. Dr. Jürgen Fritz
    \item {\sl  Rakina  Yaneva:}   `` Cloning, expression, and purification of murine tapasin in E. coli" \\ Examiners:     Prof. Dr. Martin Zacharias,   Prof. Dr. Sebastian Springer

\end{enumerate}
\paragraph{Communications, Systems and Electronics}
\begin{enumerate}
    \item {\sl  Mostafa Afgani: } ``On User Scheduling in the Downlink of a Cellular OFDMA System" \\ Examiners:     Prof. Dr. Harald Haas,   Dr. Gunther Auer
    \item {\sl  Sudharsan   Ganesan: } ``On the Performance of Spatial Modulation OFDM" \\ Examiners:     Prof. Dr. Harald Haas,   Dr. Mathias Bode
     \item {\sl  Abdurazak   Mudesir: } ``Analytical derivation of the pdf of the signal to interference ratio(SIR) in a cross layer environment under Nakagam-m distribution fading envelop. " \\ Examiners:     Prof. Dr. Harald Haas,    Dr. Mathias Bode
    \item {\sl  Nandhavel   Sethubalasubramanian: } ``Design of low power SIMD shufflers using Datapath Generator " \\ Examiners:     Prof. Dr. Werner Bergholz,   Dr. Franky Catthoor
\end{enumerate}
\paragraph{Geo-Ocean Dynamics}
\begin{enumerate}
    \item {\sl  Serkan  Kulkaksiz: } ``The Bahviour of Anthropogenic Gd in Comparison with Natural Rare Earth Elements and Yttrium in the Weser Estuary" \\ Examiners:     Prof. Dr. Michael Bau,   Prof. Dr. Andrea Koschinsky-Fritsche
    \item {\sl  Prasesh Sharma: } ``Potential correlation of heavy metal contamination in surface soils with infestation of viscum album in poplar trees in Goslar using a micro-ecosystem study" \\ Examiners:     Prof. Dr. Andrea Koschinsky-Fritsche,   Prof. Dr. Dr. Ewald Schnug
    \item {\sl  Aryani  Sumoondur: } ``Amino acids and primary amines in seawater and hydrothermal fluids from the Mid-Atlantic Ridge: Implications for metal-amino acid interactions" \\ Examiners:     Prof. Dr. Andrea Koschinsky-Fritsche,   Dr: Christian Ostertag-Henning
\end{enumerate}

\paragraph{Nanomolecular Science}
\begin{enumerate}
    \item {\sl  Supriya Babu: } ``Novel methods of preparation of Liposome-Based Nanocapsules" \\ Examiners:     Prof. Dr. Mathias Winterhalter,   Prof. Dr. Jürgen Fritz
    \item {\sl  Tivadar Mach: } ``Translocation through nanopores via an internal binding site" \\ Examiners:     Prof. Dr. Mathias Winterhalter,   Prof. Dr. Jürgen Fritz
    \item {\sl  Ahson   Shaikh: } ``One-Pot Asymmetric Sequential Amination-Alkylation Methodology: Synthesis of Chiral Amines" \\ Examiners:     Prof. Dr. Thomas Nugent,   Prof. Dr. Werner Nau
\end{enumerate}

\paragraph{Smart Systems}
\begin{enumerate}
   \item {\sl  Horia   Balan: } ``An Experimental Evaluation of
Voice-over-IP Quality over the Datagram Congestion Control Protocol"
\\ Examiners:     Prof. Dr. Jürgen Schönwälder, Prof. Dr. Michael
Kohlhase  ,   Dr. Lars Eggert
\item {\sl  Hamed   Bastani: } ``Absolute 3D Indoor Radio Positioning
Using Dynamic Roles Assignment" \\ Examiners:     Prof. Dr. Stefano
Carpin,   Prof. Dr. Harald Haas
\item {\sl
Gorkem  Erinc: } ``Nonholonomic Motion Planning Using Genetic
Algorithms for Car-Like Robots" \\ Examiners:     Prof. Dr. Stefano
Carpin,   Prof. Dr. Andreas Birk

 \item {\sl Andreas Kolling: } ``Multirobot Cooperation for Surveillance of
Multiple Moving Targets - An Improved Behavioral Approach and Its
Formalization" \\ Examiners:     Prof. Dr. Stefano Carpin, Prof. Dr.
Herbert Jaeger
   \item {\sl  Seongchu    Lee: } ``Localization
and map building in volumetric modeling for autonomous mobile robots
" \\ Examiners:     Prof. Dr. Andreas Birk, Prof. Dr. Stefano Carpin
   \item {\sl  Mantas Lukosevicius: } ``
Improving Echo State Networks by Training Intermediate Units" \\
Examiners:     Prof. Dr. Herbert Jaeger ,   Dr. Mathias Bode
\end{enumerate}


\shorttitle{PhD Degrees} \subsection{PhD Degrees}

\paragraph{Mathematical Sciences}

\begin{enumerate}
\item {\sl Alexandra Kaffl:}
 ``Hubbard Trees and Kneading Sequences for Unicritical and Cubic Polynomials''
\\ Dissertation Committee: Prof. D.
Schleicher (supervisor), Prof. M. Stoll, Prof. R. O. Wells, Prof. J.
Milnor, Prof. M. Rees, Prof. H. Bruin
\item {\sl Johannes R\"{u}ckert:}
``Newton's Method as a Dynamical System''
\\ Dissertation Committee: Prof.  D. Schleicher (supervisor), Prof. M. Oliver, Prof.
R. O. Wells, Prof. M. Lyubich, Prof. H. Bruin
\end{enumerate}

\paragraph{Chemical Sciences}

\begin{enumerate}
\item {\sl Firasat Hussain:}
``Hybrid Organic-Inorganic Polyoxometalates Functionalized by
Diorganotin Groups''
\\ Dissertation Committee: Prof. U. Kortz (supervisor), Dr. M. Dickmann,
Prof. E. Cadot, Prof. M. Pope
\item {\sl Annette Wensing:}
 ``Siderophore Production of {\sl Pseudomonas syringae} and its Implications
 on the Biological Control of Bacterial Blight of Soybean''  \\
 Dissertation Committee: Prof. M. Ullrich (supervisor), Prof. U.
Schwaneberg, Prof. G. Muskhelishvili, Prof. B. V\"{o}lksch
\item {\sl Alexander Kraynov:}
    ``Preparation and Characterization of Pt and Pd Nanoclusters Modified with
    Chiral Ligands: Examination of Catalytic Activity in Hydrogenation of Ethyl
    Pyruvate'' \\ Dissertation Committee: Prof. R. Richards (supervisor), Prof.
T. Nugent, Prof. S. Tautz
\item {\sl Harekrushna Sahoo:}
   ''Investigation of Structural, Conformational, and Dynamic
   Properties of Polypeptide by Fluorescence-Based Techniques''
   Dissertation Committee: Prof. W. Nau (supervisor), Prof. M.
   Zacharias, Prof. T. Nugent, Prof. X. Zang
\item {\sl Tuck Seng Wong:}
   ''Expanding the Toolbox of Directed Evolution for Understanding
   Protein Structure-Function Relationships''
   Dissertation Committee: Prof. U. Schwaneberg (supervisor), Dr. D.
   Roccatano, Prof. M. Zacharias, Prof. K-E. Jaeger
\end{enumerate}

\paragraph{Life Sciences}

\begin{enumerate}
\item {\sl Kristina Mayer:} ``Cathepsins during Intestinal Trauma''
\\ Dissertation Committee: Prof. K. Brix (supervisor), Prof. A. Lerchl, Prof.
A. Baici
\item {\sl Silvia Jordans:}
 ``Localization, Trafficking and functional Role of Cysteine Cathepsins in Thyroid Epithelial Cells'' \\
Dissertation Committee:   Prof. K. Brix (supervisor), Dr. D. Buttle,
Prof. A. Lerchl
\item  {\sl Brit Wolters:}
    ``Cathepsins L and V in human Keratinocytes''
\\ Dissertation Committee:  Prof. K. Brix (supervisor),
Prof. M. Ullrich, Prof. A. Lerchl, Dr. D. Buttle
\item {\sl Heiko B\"{u}th:}
 ``Contribution of Lysosomal Cystein Protease Cathepsin B to Extracellular Matris
 remodeling during Keratinocyte Migration and Wound Healing''
\\ Dissertation Committee: Prof. K. Brix (supervisor), Prof.
Boukamp, Prof. A. Lerchl, Prof. M. Ullrich
\item {\sl Karen Hinsch:}
 ``Analysis of Proliferation, Fate and Stem Cell Characteristics of Newly Generated
 Cells in the Adult Fish Brain''
\\ Dissertation Committee: Prof. G. K. H Zupanc (supervisor), Prof.
C. Hilgetag, Prof. S. Thanos
\item {\sl Marcus Lindemann:}
 ``Membrane-Protein Matrix for Technical Application''
\\ Dissertation Committee: Prof. M. Winterhalter (supervisor), Prof. J. Fritz,
Prof. V. Wagner, Prof. E. Schleif
\item {\sl Hong Qu:} ``Significance of Cathepsins B, D and L for Homeostasisof the Small Intestine''
\\ Dissertation Committee: Prof. K. Brix (supervisor), Prof. S. Springer, Prof. M. Ullrich,
Prof. G. van Echten-Deckert
%\item {\sl Mouyu Yang:}
%   ``An Investigation of the Relationships among Light, Vision Signal and Reproduction
%   on Specified Vertebrates and Invertebrates'' \\ Dissertation Committee:
%   Prof. A. Lerchla (supervisor), Prof. K. Brix, Prof. M. Bergmann
\item {\sl Christian Keithahn:}
   ''Radical Scavenging Behavior of Biogenic Amines'' \\
   Dissertation Committee: Prof. A. Lerchl (supervisor), Prof. K.
   Brix, Prof. M. Zacharias, Prof. L. Rensing
\item {\sl Chris Andr\'{e} W\"{u}rdemann:}
   ''Method Development for Expression Profiling in Prokaryotes and
   their Application in Marine Environments'' \\
   Dissertation Committee: Prof. F. O. Gl\"{o}ckner (supervisor), Prof. G.
   Muskhelishvili, Prof. M. Ullrich, Prof. R. Amman
\item {\sl Ziwei Zhu:}
   ''Making Glucose Oxidase fit for Biofuel Cell Applications by
   Directed Protein Evolution''
   Dissertation Committee: Prof. U. Schwaneberg (supervisor), Prof.
   M. Zacharias, Prof. M. Fernandez-Lahore, Prof. V. Hass
\item {\sl Joana Pereira da Silva Gomes:}
   ''Liposomes for Biosensing''
   Dissertation Committee: Prof. M. Winterhalter (supervisor), Prof.
   J. Fritz, Prof. D. Gabel
\item {\sl Stoyan Kurtev:}
   ''Lateralization of Spatial Attention in Human Brain: A 'Virtual Lesion' Approach''
   Dissertation Committee: Prof. C. Hilgetag (supervisor), Prof. B. Olk, Prof. Valero-Cabre
\end{enumerate}
