\shorttitle{PhD Degrees}
\section{PhD Degrees}

\paragraph{Mathematical Sciences}

\begin{enumerate}
\item {\sl Alexandra Kaffl:}
 ``Hubbard Trees and Kneading Sequences for Unicritical and Cubic Polynomials''
\\ Dissertation Committee: Prof. D.
Schleicher (supervisor), Prof. M. Stoll, Prof. R. O. Wells, Prof. J.
Milnor, Prof. M. Rees, Prof. H. Bruin
\item {\sl Johannes R\"{u}ckert:}
``Newton's Method as a Dynamical System''
\\ Dissertation Committee: Prof.  D. Schleicher (supervisor), Prof. M. Oliver, Prof.
R. O. Wells, Prof. M. Lyubich, Prof. H. Bruin
\end{enumerate}

\paragraph{Chemical Sciences}

\begin{enumerate}
\item {\sl Firasat Hussain:}
``Hybrid Organic-Inorganic Polyoxometalates Functionalized by
Diorganotin Groups''
\\ Dissertation Committee: Prof. U. Kortz (supervisor), Dr. M. Dickmann,
Prof. E. Cadot, Prof. M. Pope
\item {\sl Annette Wensing:}
 ``Siderophore Production of {\sl Pseudomonas syringae} and its Implications
 on the Biological Control of Bacterial Blight of Soybean''  \\
 Dissertation Committee: Prof. M. Ullrich (supervisor), Prof. U.
Schwaneberg, Prof. G. Muskhelishvili, Prof. B. V\"{o}lksch
\item {\sl Alexander Kraynov:}
    ``Preparation and Characterization of Pt and Pd Nanoclusters Modified with
    Chiral Ligands: Examination of Catalytic Activity in Hydrogenation of Ethyl
    Pyruvate'' \\ Dissertation Committee: Prof. R. Richards (supervisor), Prof.
T. Nugent, Prof. S. Tautz
\item {\sl Harekrushna Sahoo:}
   ''Investigation of Structural, Conformational, and Dynamic
   Properties of Polypeptide by Fluorescence-Based Techniques''
   Dissertation Committee: Prof. W. Nau (supervisor), Prof. M.
   Zacharias, Prof. T. Nugent, Prof. X. Zang
\item {\sl Tuck Seng Wong:}
   ''Expanding the Toolbox of Directed Evolution for Understanding
   Protein Structure-Function Relationships''
   Dissertation Committee: Prof. U. Schwaneberg (supervisor), Dr. D.
   Roccatano, Prof. M. Zacharias, Prof. K-E. Jaeger
\end{enumerate}

\paragraph{Life Sciences}

\begin{enumerate}
\item {\sl Kristina Mayer:} ``Cathepsins during Intestinal Trauma''
\\ Dissertation Committee: Prof. K. Brix (supervisor), Prof. A. Lerchl, Prof.
A. Baici
\item {\sl Silvia Jordans:}
 ``Localization, Trafficking and functional Role of Cysteine Cathepsins in Thyroid Epithelial Cells'' \\
Dissertation Committee:   Prof. K. Brix (supervisor), Dr. D. Buttle,
Prof. A. Lerchl
\item  {\sl Brit Wolters:}
    ``Cathepsins L and V in human Keratinocytes''
\\ Dissertation Committee:  Prof. K. Brix (supervisor),
Prof. M. Ullrich, Prof. A. Lerchl, Dr. D. Buttle
\item {\sl Heiko B\"{u}th:}
 ``Contribution of Lysosomal Cystein Protease Cathepsin B to Extracellular Matris
 remodeling during Keratinocyte Migration and Wound Healing''
\\ Dissertation Committee: Prof. K. Brix (supervisor), Prof.
Boukamp, Prof. A. Lerchl, Prof. M. Ullrich
\item {\sl Karen Hinsch:}
 ``Analysis of Proliferation, Fate and Stem Cell Characteristics of Newly Generated
 Cells in the Adult Fish Brain''
\\ Dissertation Committee: Prof. G. K. H Zupanc (supervisor), Prof.
C. Hilgetag, Prof. S. Thanos
\item {\sl Marcus Lindemann:}
 ``Membrane-Protein Matrix for Technical Application''
\\ Dissertation Committee: Prof. M. Winterhalter (supervisor), Prof. J. Fritz,
Prof. V. Wagner, Prof. E. Schleif
\item {\sl Hong Qu:} ``Significance of Cathepsins B, D and L for Homeostasisof the Small Intestine''
\\ Dissertation Committee: Prof. K. Brix (supervisor), Prof. S. Springer, Prof. M. Ullrich,
Prof. G. van Echten-Deckert
\item {\sl Mouyu Yang:}
   ``An Investigation of the Relationships among Light, Vision Signal and Reproduction
   on Specified Vertebrates and Invertebrates'' \\ Dissertation Committee:
   Prof. A. Lerchla (supervisor), Prof. K. Brix, Prof. M. Bergmann
\item {\sl Christian Keithahn:}
   ''Radical Scavenging Behavior of Biogenic Amines'' \\
   Dissertation Committee: Prof. A. Lerchl (supervisor), Prof. K.
   Brix, Prof. M. Zacharias, Prof. L. Rensing
\item {\sl Chris Andr\'{e} W\"{u}rdemann:}
   ''Method Development for Expression Profiling in Prokaryotes and
   their Application in Marine Environments'' \\
   Dissertation Committee: Prof. F. O. Gl\"{o}ckner (supervisor), Prof. G.
   Muskhelishvili, Prof. M. Ullrich, Prof. R. Amman
\item {\sl Ziwei Zhu:}
   ''Making Glucose Oxidase fit for Biofuel Cell Applications by
   Directed Protein Evolution''
   Dissertation Committee: Prof. U. Schwaneberg (supervisor), Prof.
   M. Zacharias, Prof. M. Fernandez-Lahore, Prof. V. Hass
\item {\sl Joana Pereira da Silva Gomes:}
   ''Liposomes for Biosensing''
   Dissertation Committee: Prof. M. Winterhalter (supervisor), Prof.
   J. Fritz, Prof. D. Gabel
\item {\sl Stoyan Kurtev:}
   ''Lateralization of Spatial Attention in Human Brain: A 'Virtual Lesion' Approach''
   Dissertation Committee: Prof. C. Hilgetag (supervisor), Prof. B. Olk, Prof. Valero-Cabre
\end{enumerate}

%\newpage
\shorttitle{Faculty}
\section{Faculty}
\begin{longtable}{ll}
Antoulas, Athanasios C., Ph.D.&Visiting Professor of Electrical Engineering  \\
Dr. Baier, Stephan& Visiting Lecturer in Mathematics \\
Dr. Bau, Michael& Associate Professor of Geosciences\\
Dr. Baumann, Peter& Associate Professor of Computer Science \\
Dr. Belov, Alexei& Visiting Professor of Mathematics \\
Dr. Bergholz, Werner& Professor of Electrical Engineering \\
Dr. Bijma, Jelle& Adjunct Professor of Marine Geosciences \\
Dr. Birk, Andreas& Associate Professor of Computer Science  \\
Dr. Bode, Mathias& Lecturer of Electrical Engineering \\
Dr. Boetius, Antje& Associate Professor of Microbiology  \\
Dr. Brix, Klaudia& Associate Professor of Cell Biology \\
Br\"uggen, Marcus, Ph.D.&Assistant Professor of Astrophysics \\
Dr. Carpin, Stefano& Assistant Professor of Computer Science \\
Fern\`{a}ndez-Lahore, Marcelo, Ph.D.&Associate  Professor of Downstream-Processing \\
Dr. Fritz, J\"urgen& Assistant Professor of Biophysics \\
Dr. Gl\"ockner, Frank Oliver& Associate Professor of Bioinformatics  \\
Haas, Harald, Ph.D.&Associate  Professor of Electrical Engineering \\
Dr. Henkel, Werner& Professor of Electrical Engineering \\
Hilgetag, Claus C.,Ph.D.&Assistant Professor of Neuroscience \\
Dr. H\"{u}tt, Marc-Thorsten& Associate Professor of Computational Systems Biology \\
Dr. Jaeger, Herbert& Associate Professor of Computational Science\\
Dr. Jeltsch, Albert& Associate Professor of Biochemistry \\
Dr. Kaimanovich, Vadim& Professor of Mathematics \\
Dr. Khalili, Arzhang& Professor of Computational Science \\
Dr. Kleinekath\"{o}fer, Ulrich& Associate Professor of Physics \\
Dr. Knipp, Dietmar& Assistant Professor of Electrical Engineering \\
Dr. K\"ohler, Angela& Adjunct Professor of Marine Biology \\
Dr. Kohlhase, Michael& Professor of Computer Science \\
Kortz, Ulrich, Ph.D.&Associate Professor of Chemistry \\
Dr. Koschinsky-Fritsche, Andrea& Associate Professor of Geosciences \\
Dr. K\"uhl, Nicole& Research Instructor (Biochemistry \& Cell Biology) \\
Dr. Kuhnert, Nikolai& Associate Professor of Chemistry \\
Dr. Lerchl, Alexander& Professor of Biology \\
Dr.-Ing Linsen, Lars& Associate Professor of Computer Science and
Computational Science \\
Dr. L\"{o}we, Astrid& Research Assistant in Physics\\
Dr.-Ing Mahleko, Bendick& University Lecturer of Electrical
Engineering \\
Mallahi-Karai, Keivan, Ph.D.&Visiting Lecturer of Mathematics \\
Dr. Materny, Arnulf&  Professor of Chemical Physics  \\
Dr. Meyer-Ortmanns, Hildegard&  Professor of Physics  \\
Meyer-Rochow, V. Benno, Ph.D., D.Sc. &Professor of Biology  \\
Dr., Muskhelishvili, Georgi& Professor of Genetics \\
Dr. Nau, Werner& Professor of Chemistry \\
Nugent, Thomas, Ph.D.&Assistant Professor of Chemistry  \\
Oliver, Marcel, Ph.D.&Assistant Professor of Mathematics \\
Dr. Oswald, Peter& Professor of Mathematics \\
Dr. Penkov, Ivan& Professor of Mathematics \\
Pfander, G\"otz, Ph.D.&Assistant Professor of Mathematics \\
Richards, Ryan M., Ph.D.&Assistant Professor of Chemistry \\
Dr. Roccatano, Danilo& University Lecturer of Chemistry \\
Dr. Rohlfing, Michael& Associate Professor of Physics  \\
Dr. Rosswog, Stephan& Assistant Professor of Astrophysics \\
% \end{longtable}
% \newpage
% \begin{longtable}{ll}
Schleicher, Dierk , Ph.D.&Professor of Mathematics  \\
Dr. Sch\"onwä\"alder, J\"urgen& Associate Professor of Computer
Science \\
Schupp, Peter , Ph.D.&Professor of Physics  \\
Dr. Schwaneberg, Ulrich& Assistant Professor of Biochemical Engineering \\
Springer, Sebastian,D. Phil. &Assistant Professor of Biochemistry and Cell Biology\\
Dr. Stamerjohanns, Heinrich& Research Assistant, Head of CS Lab \\
Dr. Stoll, Michael& Associate Professor of Mathematics \\
Dr. Styrkas, Konstantin& Visiting Assistant Professor of Mathematics \\
Tautz, Stefan , Ph.D.&Associate Professor of Physics \\
Dr. Thomsen, Laurenz& Associate Professor of Geosciences \\
Dr. Ullrich, Matthias& Professor of Microbiology \\
Unnithan, Vikram, Ph.D.&Assistant Professor of Geoscience \\
Dr. Vogt, Joachim& Associate Professor of Physics \\
Dr. Wagner, Veit&  Associate Professor of Physics \\
Wallace, Jon, Ph.D.&Assistant Professor of Electrical Engineering \\
Wells, Raymond O. , Ph.D.&Distinguished Professor of Mathematics  \\
Dr. Welte, Dietrich& Adjunct Professor of Geosciences \\
Dr. Wiltshire, Karen Helen& Full Professor of Geoscience - AWI\\
Dr. Winterhalter, Mathias& Professor of Biophysics  \\
Dr. Zacharias, Martin& Associate Professor of Computational Biology \\
Zupanc, G\"unther K. H.,Ph.D.&Professor of Neurobiology       \\

\end{longtable}

\shorttitle{Staff}
\section{Staff}
\begin{longtable}{ll}
Abu-Alhiga, Rami & Integrated PhD Student (EE)\\
Afgani, Mostafa & Research Associate (EE) \\
Al-Buloshi, Mohammed & Graduate Student (BCE)\\
Al-Karablieh, Nehaya & Graduate Student (Microbiology)\\
Al-Shbat, Shering & Integrated PhD Student (CS)\\
Alexander, Brian & Graduate Student (Geology/Geochemistry)\\
Dr. Allner, Anke-Maria & Assistant to the Dean \\
Bakirci, Huseyin & Graduate Student (Chemistry)\\
Dr. Balster, Torsten & Research Associate\\
Bassil, Bassem & Graduate Student (Nanomolecular Science)\\
Becker, Sandra & Lab Assistant (Biology)\\
Behnke, Torsten & Technician, Ocean Lab\\
Benor, Amare & Graduate Student (Electrical Engineering)\\
Berger, Michael & Graduate Student (Biochemistry)\\
Bharucha, Zubin & Integrated PhD Student (EE) \\
Binner, Sabine & Research Assistant (Biochemical Engineering)\\
Blanusa, Milan & Graduate Student (BCE)\\
Dr. Blohmann, Christian & Postdoctoral Fellow (Physics)\\
Borchert, Britta & Graduate Student (Biochemistry)\\
Braun, Yvonne & Research Associate/Graduate Student (Microbiology)\\
B\"{u}th, Heiko & Graduate Student (Cell Biology)\\
Burau, Claudia & Lab Assistant (Biochemistry)\\
Caballero Hern\'{a}ndez, Josefa & Graduate Student (Biochemical Engineering)\\
Cabrera, Rosa & Postdoctoral Fellow (Downstream Processing) \\
Chahar, Sanjay & Graduate Student (Biochemistry)\\
Chan, Kah-Yoong & Graduate Student (Electrical Engineering)\\
%                    \end{longtable}
%                   \newpage
%                   \begin{longtable}{ll}
Chonnaparamutt, Winai & Graduate Student (Computer Science)\\
Chubarova, Elena, Ph.D. & Postdoctoral Fellow (Chemistry) \\
Claus, Ute & Lab Assistant (Biochemistry) \\
Curusku, Jeremy & Research Associate (Computational Biology) \\
Dairpoosh, Farnoosh& Graduate Student (BCE) \\
Dammann, Frauke & IMO Assistant (Mathematics)\\
Dan, Marius & Graduate Student (Astrophysics) \\
de Jesus Mendes, Pedro Andr\'{e} & Graduate Student (Geosciences)\\
Dr. Dehnert, Manuel& Postdoctoral Fellow (Computational Systems Biology) \\
Dhayalan, Arunkumar & Graduate Student (Biochemistry)\\
Dickman, Michael, Ph.D. & Senior Research Associate (Chemistry)\\
Dinkel, Thomas & Graduate Student (EE) \\
Donfack, Patrice & Graduate Student (Chemical Physics) \\
Donnelly, Stephen & Postdoctoral Fellow (Mathematics) \\
Dunkhorst, Anna & Graduate Student (Cell Biology) \\
Ehlers, Birte-Marie & Graduate Student (Geosciences)\\
El-Sheshtawy, Hamdy & Graduate Student (Chemistry) \\
Elgala, Hany & Lab Assistant (Electrical Engineering) \\
Dr. Frischholz, Svenja & Assistant (Administration Graduate Students)\\
Felden, Janine & Graduate Student (Marmic) \\
Fu, Yanzhe & Graduate Student (Geosciences) \\
Gama Saldago, Antonio & Research Associate (Neurobiology) \\
Garcia Gutierrez, Angelica & Graduate Student (Computer Science) \\
Garcia-Novoa, Rosa & Graduate Student (GeoOcean Dynamics)\\
Garstka, Malgorzata & Graduate Student (Biochemistry)\\
Gburek, Benedikt & Research Associate and Graduate Student (Physics) \\
Geberth, Daniel & Graduate Student (Computational Systems Biology) \\
Geertz, Marcel & Graduate Student (Biochemistry)\\
Gelessus, Achim & CLAMV Server Manager\\
Ghimire, Birendra & Graduate Student (EE) \\
Gobet, Angelique & Graduate Student (Marmic)\\
Ghosh, Abhijit & Graduate Student (Chemistry)\\
Grote, Karen & Technical Assistant (Biology)\\
Guimbretiere, Thomas & Graduate Student (Astrophysics) \\
Hanelt, Sharifah Nora & Research Associate (Geosciences) \\
Hassan, Khaled & Research Associate (Electrical Engineering)\\
Hassanin, Rasha & Graduate Student (Chemical Physics) \\
Hauschildt, Jakob & Graduate Student (Geophysics)\\
Dr. Helling, Robert & Research Associate (Physics)\\
Hennig, Andreas & Graduate Student (Chemistry) \\
Dr. Henze, Stina & Research Associate (Physics)\\
Hinsch, Karen & Graduate Student (Neuroscience)\\
Dr. Hoeft, Matthias & Postdoctoral Fellow (Astrophysics)\\
Hofbauer, Michael & Electronic Technician (Ocean Lab)\\
Holzapfel, Christine & Lab Assistant Chemistry\\
Hoppe, Arne & Graduate Student (Physics)\\
Hu, Fangning & Graduate Student (Electrical Engineering)\\
Dr. Hu, Jun-Cheng & Postdoctoral Fellow (Chemistry) \\
Hussain, Firasat & Graduate Student (Chemistry)\\
Ihle, Saskia & Graduate Student (BCE)\\
Ismail, Amal & Graduate Student (Chemistry)\\
Ivanovska, Tetyana & Graduate Student (CS)\\
Jordans, Silvia & Graduate Student (Cell Biology)\\
Josuttis, Daniela & Lab Technician (Biochemical Engineering)\\
Jurkowski, Renata & Graduate Student and Research Associate (Biochemistry)\\
Jurkowski, Thomasz & Graduate Student (Biochemistry)\\
Kaffl, Alexandra & Graduate Student (Mathematics)\\
von der Kammer, Bernd& Lab Assistant Physics \\
Kannan, Srinivasaraghavan & Research Associate (Biology) \\
Dr. Karpen, Volker & Research Associate (Oceanography)\\
%\end{longtable} \newpage
%\begin{longtable}{ll}
Keithahn, Christian & Graduate Student (Biology)\\
Klepsch, Meike & Lab Assistant (Biochemistry and Cell Biology) \\
Klose, Melanie & Graduate Student (Biology) \\
Knoop, Katja& Team Assistant to the Faculty \\
Kohlhase, Andrea & Guest (CS)\\
Kolyuzhov, Dennis & Graduate Student (Electrical Engineering)\\
Konradi, Jakow & Graduate Student (Physics)\\
Kottmann, Renzo & Graduate Student (Marine Microbiology)\\
Kraynov, Alexander & Graduate Student (Chemistry)\\
Kronenberger, Astrid & Graduate Student (Physics)\\
Kurtev, Stoyan & Graduate Student (Neuroscience)\\
Dr. Laser, Heike & Postdoctoral Fellow (Biology)\\
Laskowski, Katja & Lab Assistant (Biochemistry \& Cell Biology)\\
Lau, Tin Fan Stanley & Graduate Student (Biology)\\
Laubner, Bastian & Integrated PhD Student (Mathematics) \\
Liebert, Kirsten & Research Associate, Graduate Student (Biochemistry)\\
Limmanee, Apirath & Graduate Student (EE)\\
Lindemann, Marcus & Graduate Student (BCE)\\
Dr. Linnenberg, Susanne & Research Assistant (Teaching Lab Physics)\\
Linow, Marina & Research Associate (BCE)\\
Lucosevicius, Mantas & Graduate Student (CS)\\
Mal, Sibsankar & Graduate Student (Chemistry)\\
Manss, Sigrid & Team Assistant to the Faculty\\
Marbler, Herwig & Research Associate (Geosciences)\\
Maurer, Sebastian & Graduate Student (Biochemistry)\\
Mavathur, Ramesh & Graduate Student (Biochemistry)\\
Mawick, Jule & Lab Assistant (Geoscience)\\
May, Andreas & Graduate Student (BCE)\\
Mayer, Kristina & Graduate Student (Cell Biology)\\
Mei\ss ner, Daniela & Technical Assistant (Biology)\\
Mesleh, Read & Graduate Student (EE)\\
Mishra, Monalisa & Graduate Student (Biology)\\
Moje, Annika & Lab Assistant (Geoscience) \\
Molchanov, Vladimir  & Graduate Student (Mathematics) \\
Momeu, Iuliana Carmen & Graduate Student (BCE)\\
Mudesir, Abdurazak & Graduate Student (EE)\\
M\"uller, Christine & Graduate Student (CS)\\
M\"uller, Jan Steffen & Graduate Student (Mathematics)\\
M\"uller, Normen & Graduate Student (Computer Science) \\
M\"uller-Linow, Mark & Graduate Student (Computational Systems Biology)\\
Namboodiri, Vinu & Graduate Student (Chemical Physics)\\
Nazor, Jovanna & Graduate Student (BCE) \\
Neu, Florian & IRCCM/CLAMV Systems Administrator\\
Nour Abdel-Gawad Ahmed, Mohammed & Graduate Student (CS)\\
Normann, Immanuel & Graduate Student (Computer Science)\\
Nsouli, Nadeen & Graduate Student (Chemistry) \\
Dr. Omiyi, Peter & Postdoctoral Fellow (Electrical Engineering)\\
Onaca, Ozana & Graduate Student (Biochemical Engineering)\\
Pagel, Uwe & Electrical Engineering \& Computer Science Technician\\
Pankratz, Elke & Team Assistant to the Faculty\\
Pathak, Kaustubh, Ph.D. &Postdoctoral Fellow (CS) \\
%                   \end{longtable} \\
%                   \newpage
%                   \begin{longtable}{ll}
Pereira Da Silva Gomes, Joana Filipa & Postdoctoral Fellow (Biophysics)\\
Pezeshki, Soroosh & Graduate Student and Research Associate (Physics)\\
Pfingsthorn, Max & Graduate Student (CS)\\
Piedra-Garza, Luis & Graduate Student (Chemistry)\\
Poppescu, Traian & Graduate Student (Astrophysics)\\
Poppinga, Jann & Graduate Student (CS)\\
Prabhakar, Rajendran & Graduate Student (Nanomolecular Science)\\
Praeg, Daniel, Ph.D. & Research Associate (Geosciences)\\
Prodanovic, Radivoje, Ph.D. & Postdoctoral Fellow (BCE)\\
Purser, Autun & Integrated PhD Student (Geosciences)\\
Qu, Hong & Graduate Student (Cell Biology)\\
Rabe, Florian & Graduate Student (EECS)\\
Radicchi, Filippo & Graduate Student (Physics)\\
Dr. Ragozin, Sergey & Postdoctoral Fellow (Biochemistry)\\
Rajendran, Raphael Samuel & Graduate Student (Neurosciences)\\
Dr. Ramaye, Yannic & Postdoctoral Fellow (Biophysics)\\
Rashkov, Peter & Graduate Student (Mathematics)\\
Rathert, Philipp & Graduate Student (Biochemistry)\\
Rehders, Maren & Lab Assistant (Biochemistry and Cell Biology)\\
Reicke, Markus & Lab Assistant (Chemistry)\\
Dr. R\"{o}diger, Elke & Research Associate (Astrophysics)\\
Rohde, Christian & Graduate Student (Biochemistry)\\
Rosenk\"{o}tter, Frank & Lab Assistant (Physics)\\
Rosenthal, Paul & Graduate Student (CS)\\
R\"{u}ckert, Johannes & Graduate Student (Mathematics)\\
Rulli, Matteo & Graduate Student (Physics)\\
Sahoo, Harekrushna & Graduate Student (Chemistry)\\
Santillano, Daniel & Graduate Student (Marmic)\\
Scaria, Abraham & Graduate Student (Physics)\\
Sch\"{a}fer, Angela & Research Associate (IRCCM)\\
Dr. Schirmer, Thomas & Research Associate (Geosciences)\\
Schlickenrider, Martina & Research Associate (Biochemistry)\\
Schmidt, Katja & Graduate Student (Geoscience)\\
Schneewei{\ss}, Clemens & Research Associate (Biochemistry)\\
Schreiber, Angela & Office of the Dean\\
Schr\"{o}der, Markus & Graduate Student and Research Associate (Physics)\\
Schwarzlose, Thomas & Research Assistant, Teaching Lab Chemistry\\
Dr. Schwarzpaul, Kristin & Research Associate (Biology)\\
Schwerdtfeger, Maike & Lab Assistant Biochemistry \\
Schwertfeger, S\"{o}ren & Graduate Student (CS)\\
Shaik, Mona & Visiting Graduate Student (EE)\\
Sieker, Florian & Graduate Student (BICB)\\
Sharma, Praseh & Graduate Student (Geosciences)\\
Simon, Tatjana & Technical Assistant (Biology)\\
Dr. Solodukhin, Sergey N. & Senior Research Associate (Physics)\\
Dr. Sommer, Angela & Research Associate (Biology)\\
Dr. Soubatch, Serguei & Research Associate (Physics)\\
Sourly-Gopala, Divakara & Graduate Student (Chemistry)\\
Srivastava, Abhishek & Graduate Student (BioRec)\\
Stroehlein, Thomas & Animal Keeper\\
Suchopar, Andreas & Lab Assistant Chemistry \\
Tayakuniyil, Praveen & Graduate Student (Biochemistry)\\
Tee, Kang Lan & Graduate Student (Biochemical Engineering)\\
Temirov, Ruslan & Graduate Student (Nanomolecular Science)\\
Thomsen, Claudia & Research Associate (Oceanography) \\
% \end{longtable}
%                   \newpage
%                   \begin{longtable}{ll}
Thon, Michael & Graduate Student (Mathematics)\\
T\"{o}mmers, Stephanie & Graduate Student (BCE)\\
Tran, Ha Manh & Graduate Student (CS)\\
Tran, Que-Tien & Graduate Student (Biophysics)\\
Tran, Van Long & Graduate Student (CS)\\
Vennapusa, RamiReddy & Graduate Student (BCE)\\
Venkatraman, Hrishikesh & Graduate Student (Electrical Engineering)\\
Vilone, Daniele, Ph.D. & Postdoctoral Fellow (Physics)\\
Viergutz, Thomas & Marine Technology Engineer\\
von Deetzen, Neele & Graduate Student (Electrical Engineering)\\
Wagner, Hannes & Graduate Student (Geosciences)\\
Wakchaure, Vijay & Graduate Student (Chemistry)\\
Wecker, Patricia & Graduate Student (Microbiology)\\
Wellbrock, Ursula & Research Assistant (Biology)\\
Wensing, Annette & Graduate Student (Microbiology)\\
Wong, Tuck Seng & Graduate Student (BCE)\\
Wolters, Brit & Graduate Student (Cell Biology)\\
W\"{u}rdemann, Chris Andr\'{e} & Graduate Student (Genetics)\\
Yaneva, Rakina & Graduate Student (Cell Biology)\\
Yang, Mouyu & Graduate Student (Biology)\\
You, JiangJiang & Graduate Student (Astrophysics)\\
Dr. Yu, Jin & Postdoctoral Fellow (Neuroscience)\\
Zhang, YingYing & Graduate Student (Biochemistry)\\
Zhao, Mingjie, Ph.D. & Postdoctoral Fellow (EE)\\
Zhu, Ziwei & Graduate Student (BCE)\\
Dr. Zieger, Bertalan & Postdoctoral Fellow (Physics)\\
Zieger, Marina & Postdoctoral Fellow (Biology)\\
Dr. Zupanc, Marianne & Research Associate (Neurobiology)\\
%
%                      \end{longtable}
%                  \newpage
%\begin{longtable}{ll}

\end{longtable}
%\end{center}
