\section{The Communication of Information and Knowledge: An
Important Facet of Lifelong Learning} \shorttitle{Communication of Information and Knowledge}

Media are (external) information storage devices and transmitters. Knowledge is the internal representation of information including the relations of all the components in a living being. Lifelong learning means acquiring knowledge at all stages of life. Three different kinds of knowledge - among others - can be identified: 
\begin{itemize}
	\item Procedural knowledge (e.g., setting the VCR-timer).
	\item Social and semantic knowledge (e.g., Alois Alzheimer was born in 1864). 
	\item Personal knowledge (e.g., what wartime was like).
\end{itemize}

The human species is the only species that can transfer knowledge by an elaborate system of communication. Humans learn throughout all their life, they are able to plan ahead by imagining, rehearsing and evaluating situations. Humans can do that mentally, in games and by watching or listening to others - even by reading a book, surfing the internet, listening to radio or watching TV or a movie. 

 Our overarching research question is what roles media play for lifelong learning and if age differences can be identified.

\subsection{BALANCE: The Effects of Media Communication}

\input{CommunBallance}

\newpage
\subsection{Technical Documentation: Age-related Formatting of Information}

\input{CommunTech}

\subsection{Feldpost-Archiv} 

\input{CommunFeldpost}

\subsection{\mbox{Age, Emotions and Media-Preferences}}

\input{CommunAge}

\subsection{Identification of Matches and Mismatches in Communication at the Work Place}

\input{CommunIdent}

\enlargethispage{2cm}
\subsection{Other Professional Activities}

\begin{itemize}
\item Reviewer for ICA-Conference in San Fransisco 2007.
\item Reviewer for DGPuK-Conference in Bamberg 2007.	
\end{itemize}
