\section{Emotional Competence and Wisdom: Lifespan Developmental Perspectives} \shorttitle{Adult Development of Socio-Emotional Competences
}

One-sided views of aging and old age still exist in our society as well as in scientific circles. On the one hand, old age has been portrayed as a period of disengagement, social isolation, cognitive inflexibility, and physical decline. On the other, many people, especially older people themselves have described old age as a productive life period full of energy, new and inspiring experiences, and gratifying moments. Lifespan developmental researchers have argued that images of old age and aging that are either too negative or too positive run the risk of being dysfunctional. Overly pessimistic views lead to disregard for the possibility that many older people have great potential and could provide valuable contributions to societal life. Illusory positive views put unnecessary pressure on those older people who have experienced age-related losses and hinder social policies aimed at improving their living situations.

 Adopting a lifespan developmental approach, the overarching goal of our research has been to contribute to a balanced picture of aging and old age that encompasses loss, continuity, and growth. According to lifespan developmental psychology, the complexity of developmental processes during adulthood can be described on at least four levels. First, development is multidirectional. During the same developmental period, some realms of functioning decline, while others remain stable, and yet others increase. Second, development is multifunctional. Depending on the criteria that are being considered (e.g., subjective vs. objective or long-term vs. short-term), the same developmental outcome can be considered as gain or loss. Third, development varies among individuals and various social, educational, and ethnic groups. Depending on the individual's personal and social resources, the same realm of functioning may decline, increase, or remain unchanged during adulthood and old age. Fourth, people do not exist in isolation, but are embedded in historical, cultural, and social contexts that provide both developmental opportunities and constraints.

 Two realms of functioning, which are at the center of our research, are ideally suited to demonstrate the complexity of the aging process on the four levels described above. These are emotional competence and wisdom. The primary purpose of our research is to demonstrate that the development of emotional competence and wisdom is differential. That is, it evinces multidirectionality, varies among individuals, is contextually-bound, and simultaneously involves gains and losses. This differentiated view of development helps expand and supplement more traditional conceptualizations that have emphasized universal and general developmental processes and equate development with growth. 

\subsection{Emotional Competence}

\input{CompetEmoCompet}

\subsection{Emotions in Art}

\input{CompetEmoArt}

\subsection{Wisdom}

\input{CompetWisdom}

\subsection{Awards, Fellowships}
\begin{itemize}
\item Junior Fellow of the Max Planck International Research Network on Aging. 
\end{itemize}

\subsection{Other Professional Activities}  

\begin{itemize}
\item Consultant on methods to assess physiological and behavioral aspects of emotion with NIH Project; PI: Prof. Dr. Blanchard-Fields, Georgia Institute of Technology, Atlanta.
\item Faculty member of the research network ``Differential and General Development of Emotion'' funded by the German Research Foundation (HO 1718/5-1).
\end{itemize}

\textit{Editorial Board Membership}

\begin{itemize}
\item Psychology and Aging.
\end{itemize}

\vspace{0.5ex}
\textit{Ad-hoc Reviews}

\begin{itemize}
\item Swiss National Science Foundation.
\end{itemize} 
