\section{A View on Lifelong Learning from Health and Personality
Psychology} \shorttitle{Health and Personality
}
\subsection{Health Psychology}

\input{HealthPersoHealthPsych}

\subsection{Personality Psychology}

\input{HealthPersoPersPsych}

\subsection{Other Professional Activities}

\begin{itemize}
\item President of the European Health Psychology Society (EHPS).
\item Chair of the Scientific Committee of the 20th Conference of the European Health Psychology Society in Warsaw, 2006.
\item Organizer of the Summer School of the Fachgruppe Gesundheitspsychologie der Deutschen Gesellschaft f\"{u}r Psychologie, International University Bremen, JCLL, Bremen, 2006.
\item Member of the Scientific Committee of the Fachgruppentagung Gesundheitspsychologie, Deutsche Gesellschaft f\"{u}r Psychologie, 2007.
\item Expert for the subject area ``risk perception and behavior'', Division of Health Psychology of the Deutsche Gesellschaft f\"{u}r Psychologie.
\end{itemize}

\textit{Editorial Board Memberships}

\begin{itemize}
\item European Health Psychology Review.
\item	Zeitschrift f\"{u}r Gesundheitspsychologie (Journal of Health Psychology).
\end{itemize}

\textit{Ad-hoc Reviews}

\begin{itemize}
\item Cognition and Emotion; Diagnostica; European Journal of Personality; Experimental Psychology; Journal of Individual Differences; Journal of Positive Psychology; Journal of Public Health; Memory; Psychology \& Health; Psychology, Health \& Medicine; Social Cognition; Social \& Preventive Medicine; Social Science \& Medicine; Zeitschrift f\"{u}r Gesundheitspsychologie.
\item Reviewer for DFG.
\end{itemize}
 
 
