\section{Visiting Scholars at the Jacobs Center}
\shorttitle{Visiting Scholars}

\textit{Dr. Pilvikki Absetz} (KTL Public Health Institute Helsinki, Finland)

 
\textit{Prof. Dr. Uschi Backes-Gellner} (Professor of Business Administration, University of Zurich, Switzerland): ``Demographical Change, Firm Demography and Productivity''


\textit{Dr. Lutz Bellmann} (Institut f\"ur Arbeitsmarkt- und Berufsforschung): ``Recruiting Elder Employees in Germany: Empirical Evidence from a Large-Scale Establishment Panel Survey''


\textit{Yael Benyamini, PhD} (School of Social Work, Tel-Aviv University)


\textit{Prof. Dr. Axel B\"orsch-Supan} (Professor of Macroeconomics and Public Policy, University of Mannheim, and Director, Mannheim Research Institute for the Economics of Aging - MEA): ``Macroeconomic Consequences of Demographic Change''


\textit{Dr. Hartmut Buck} (Fraunhofer Institut Arbeitswirtschaft und Organisation): ``Aging Workforce - Consequences for Enterprises''


\textit{Prof. Dr. Ekkehart Frieling} (Professor of Business Administration, University of Kassel): ``Work Conditions that Facilitate Learning''


\textit{Prof. Winifred A. Gebhardt, PhD} (Professor of Clinical and Health Psychology, Leiden University, NL)


\textit{Prof. Dr. Werner Greve} (Professor of Psychology, University of Hildesheim)


\textit{David Hevey, PhD} (School of Psychology, Trinity College Dublin)


\textit{Dr. Dagmar Hoffmann} (Academy of Film and Television, Potsdam-Babelsberg): ``Older People, Media Activities and Movie Preferences - What Does Research Tell Us?''


\textit{Prof. Arthur Kramer, PhD} (Professor of Human Performance, University of Illinois, USA, and Director of the Biomedical Imaging Center at the University of Illinois): ``Fitness Effects on Brain and Cognition''


\textit{Prof. Dr. Marius Leibold} (Professor of Strategic International Management, University of Stellenbosch, South Africa)


\textit{Prof. Dr. Susan Michie} (Professor of Health Psychology, University College London)


\textit{Prof. Dr. Ekkehart Nuissl von Rein} (Professor of Educational Science, and Scientific Director of the German Institute for Adult Education - DIE): ``Development of European Perspectives of Adult Education''


\textit{Prof. Dr. Christel Salewski} (Hochschule Magdeburg-Stendal, FH)


\textit{Dr. Caroline Schuster-Cordone} (University of Bern, Switzerland)


\textit{Prof. Dr. Norbert Schwarz} (Professor of Psychology, University of Michigan, USA): ``Would you be happier if you were younger and richer?''


\textit{Prof. Dr. Ralf Schwarzer} (Professor of Psychology, Free University of Berlin): ``How to Conceptualize Health Behavior Change: Stage Models vs. Continuum Models''


\textit{Dr. Vegard Skirbekk} (International Institute for Applied Systems Analysis, Austria): ``Productivity Potential over the Life Cycle. The Changing Importance of Age-Specific Abilities'' 


\textit{Dr. Vera Soares} (Department of Psychology, University of the Minho, Portugal)


\textit{Prof. Dr. Thomas Staufenbiehl} (Professor of Psychology, University of Osnabr\"uck)


\textit{Prof. Dr. Clemens Tesch-R\"omer} (Professor of Psychology, Free University of Berlin and Director of the German Centre of Gerontology - DZA, Berlin): ``Health in an Aging Workforce - Results from the German Aging Survey''


\textit{Irina Todorova, PhD} (Bulgarian Academy of Sciences)


\textit{Prof. Dr. Gert Wagner} (Professor of Economics, Berlin Technical University, and SOEP Research Director, Deutsches Institut f\"ur Wirtschaftsforschung): ``The German Socio-Economic Panel Study (SOEP) as a Basis for Life Course Research''


\textit{Prof. Dr. Klaus Willimczik} (Professor of Human Performance, University of Bielefeld): ``The Effectiveness of Teaching and Learning Sport Motor Skills Across the Lifespan - Theoretical and Meta-Theoretical Aspects''
